---
title: "Project Phase 2- Preliminary Analysis"
author: "Team Popcorn - Amritha, Ahana, Keerthana"
date: "05/3/2026"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
    latex_engine: xelatex
  
---
```{r}
knitr::opts_chunk$set(cache = FALSE)
```
# So we have three tasks in the MST_Data folder 
├── Both_item_task/
│   └── both_data/                # Data files for Experiment 1
├── item_only/
│   └── item_only_data/           # Data files for Experiment 2
├── task_only/
│   └── task_only_data/           # Data files for Experiment 3

# Dataset Description

The dataset used in this study is organized into three experimental conditions of the Mnemonic Similarity Task (MST): **Both Item + Task**, **Item-only**, and **Task-only**. Each condition is stored in a separate directory within the `MST_Data` folder.

Within each condition, the data is structured at the participant level. For every participant, there are two CSV files corresponding to the two phases of the experiment:

* a **task file**, representing the encoding (study) phase
* a **test file**, representing the retrieval (memory test) phase

The files follow a consistent naming convention of the form:
`<subjectID>_MST_<phase>_<date>_<timestamp>.csv`,
where the subject ID uniquely identifies each participant and the phase indicates whether the file corresponds to the encoding or test stage.

The task files primarily contain information related to stimulus presentation and encoding responses, including image paths, trial indices, and key responses recorded during the study phase.

The test files contain trial-level behavioral data used for analysis, including: 

stimulus identity (e.g., scene or object images)
stimulus condition (e.g., target, lure, foil — inferred from stimulus position/type)
participant responses (e.g., old, similar, new)
reaction times associated with each response

From these test-phase variables, key behavioral measures are computed:

LDI (Lure Discrimination Index), reflecting the ability to distinguish similar items
REC (Recognition Score), reflecting general recognition performance
Reaction Time (RT), capturing response latency

The dataset is structured such that each participant contributes multiple trials, enabling within-subject analysis of memory performance across different stimulus types.

Experiment	Condition:
1	Both (item + task boundary)
2	Item-only
3	Task-only
# Preprocessing 

```{r}

library(tidyverse)

base_path <- "../MST_Data"

clean_task_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  cat("Initial rows:", nrow(df), "\n")
  
  # -------------------------------
  # Extract participant ID
  # -------------------------------
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  # -------------------------------
  # Ensure required columns exist
  # -------------------------------
  required_cols <- c("image_path", "trials.thisN")
  
  missing_cols <- setdiff(required_cols, names(df))
  
  if(length(missing_cols) > 0){
    stop(paste("Missing columns:", paste(missing_cols, collapse=", ")))
  }
  
  # -------------------------------
  # Create RT columns if missing
  # -------------------------------
  if(!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if(!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  
  # -------------------------------
  # CLEAN
  # -------------------------------
  df_clean <- df %>%
    
    # remove non-trial rows
    filter(!is.na(trials.thisN)) %>%
    
    # remove empty image rows
    filter(!is.na(image_path), image_path != "") %>%
    
    # remove practice
    filter(!str_detect(image_path, "practice")) %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      
      # numeric safety
      rt_9 = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      rt_8 = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      
      # RT correction
      rt = case_when(
        !is.na(rt_9) ~ rt_9,
        !is.na(rt_8) ~ 3 + rt_8,
        TRUE ~ NA_real_
      ),
      
      image_name = basename(image_path)
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, rt)
  
  # -------------------------------
  # DEBUG PRINTS
  # -------------------------------
  cat("Rows after cleaning:", nrow(df_clean), "\n")
  cat("Unique images:", length(unique(df_clean$image_name)), "\n")
  cat("RT summary:\n")
  print(summary(df_clean$rt))
  
  return(df_clean)
}

# TEST PREPROCESSER
clean_test_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing TEST:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  df_clean <- df %>%
    
    filter(!is.na(trials.thisN)) %>%
    
    filter(!is.na(image_path), image_path != "") %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      image_name = basename(image_path),
      
      # classify stimulus
      stimulus_type = case_when(
        str_detect(tolower(image_path), "^foil") ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE ~ NA_character_
      ),
      
      # response mapping
      response = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE ~ NA_character_
      )
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, stimulus_type, response)
  
  # DEBUG
  cat("Rows:", nrow(df_clean), "\n")
  cat("Stimulus counts:\n")
  print(table(df_clean$stimulus_type))
  
  return(df_clean)
}

# LOAD ALL EXPEERIMENTS

load_experiment <- function(task_dir, test_dir, label) {
  
  cat("\n=============================\n")
  cat("LOADING EXPERIMENT:", label, "\n")
  
  task_files <- list.files(task_dir, pattern = "task.*\\.csv$", full.names = TRUE)
  test_files <- list.files(test_dir, pattern = "test.*\\.csv$", full.names = TRUE)
  
  cat("Task files:", length(task_files), "\n")
  cat("Test files:", length(test_files), "\n")
  
  task_data <- map_dfr(task_files, clean_task_file)
  test_data <- map_dfr(test_files, clean_test_file)
  
  task_data$experiment <- label
  test_data$experiment <- label
  
  return(list(task = task_data, test = test_data))
}

# RUN PREPROCESSING FOR ALL THREE EXPERIMENTS 

exp1 <- load_experiment(
  "../MST_Data/Both_item_task/both_data",
  "../MST_Data/Both_item_task/both_data",
  "both"
)

exp2 <- load_experiment(
  "../MST_Data/item_only/item_only_data",
  "../MST_Data/item_only/item_only_data",
  "item_only"
)

exp3 <- load_experiment(
  "../MST_Data/task_only/task_only_data",
  "../MST_Data/task_only/task_only_data",
  "task_only"
)

# Combine
task_all <- bind_rows(exp1$task, exp2$task, exp3$task)
test_all <- bind_rows(exp1$test, exp2$test, exp3$test)

cat("\nFINAL DATA SUMMARY\n")
cat("Total task rows:", nrow(task_all), "\n")
cat("Total test rows:", nrow(test_all), "\n")

# SANITY CHECK 
head(task_all)
summary(task_all$rt)
table(test_all$stimulus_type)
```

# VISUALISATION 
HOW TO USE THESE (IMPORTANT)
Check these before moving forward:
✅ Reaction Time
Right skew? → expected
Extreme outliers? → consider trimming/log transform
✅ Response Distribution
Balanced responses?
Too many “Old”? → bias issue
✅ Stimulus Types
Should roughly match:
✅ Accuracy / Hit Rate
Should be above chance (~0.5)
If not → data quality issue
✅ LDI / REC
Should be > 0 (as per MST theory)


```{r}
cat("\n================ VISUALIZATION PIPELINE ================\n")


# ---------------------------------------------------------
# 1. FIX STIMULUS CLASSIFICATION (IMPORTANT FIX)
# ---------------------------------------------------------
test_all_fixed <- test_all %>%
  mutate(
    stimulus_type = case_when(
      str_detect(tolower(image_path), "^foil") ~ "Foil",
      str_detect(image_name, "a\\.jpg$") ~ "Target",
      str_detect(image_name, "b\\.jpg$") ~ "Lure",
      TRUE ~ NA_character_
    )
  )

cat("\nStimulus distribution AFTER FIX:\n")
print(table(test_all_fixed$stimulus_type, useNA = "always"))

# ---------------------------------------------------------
# 2. CLEAN DATA (REMOVE INVALID)
# ---------------------------------------------------------
task_clean <- task_all %>%
  filter(!is.na(rt), is.finite(rt))

test_clean <- test_all_fixed %>%
  filter(!is.na(stimulus_type))

# ---------------------------------------------------------
# Custom Color Palette
# ---------------------------------------------------------
palette_main <- c(
  "Target" = "#2E86AB",
  "Lure"   = "#F18F01",
  "Foil"   = "#C73E1D"
)

palette_resp <- c(
  "Old" = "#1B998B",
  "Similar" = "#ED217C",
  "New" = "#2D3047"
)

# ---------------------------------------------------------
# 3. REACTION TIME DISTRIBUTION
# ---------------------------------------------------------
ggplot(task_clean, aes(x = rt, fill = experiment)) +
  geom_histogram(bins = 50, alpha = 0.6, color = "black") +
  geom_density(aes(color = experiment), linewidth = 1) +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = "Reaction Time Distribution", x = "RT", y = "Count") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 4. RT BOXPLOT
# ---------------------------------------------------------
ggplot(task_clean, aes(x = experiment, y = rt, fill = experiment)) +
  geom_boxplot(alpha = 0.7, outlier.color = "red") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "RT by Experiment") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 5. STIMULUS TYPE DISTRIBUTION (FIXED)
# ---------------------------------------------------------
ggplot(test_clean, aes(x = stimulus_type, fill = stimulus_type)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_main) +
  labs(title = "Stimulus Type Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 6. RESPONSE DISTRIBUTION
# ---------------------------------------------------------
ggplot(test_clean, aes(x = response, fill = response)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_resp) +
  labs(title = "Response Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 7. ACCURACY
# ---------------------------------------------------------
acc_data <- test_clean %>%
  mutate(correct = case_when(
    stimulus_type == "Target" & response == "Old" ~ 1,
    stimulus_type == "Lure" & response == "Similar" ~ 1,
    stimulus_type == "Foil" & response == "New" ~ 1,
    TRUE ~ 0
  )) %>%
  group_by(participant_id, experiment) %>%
  summarise(accuracy = mean(correct), .groups = "drop")

ggplot(acc_data, aes(x = accuracy, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Accuracy Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 8. HIT RATE
# ---------------------------------------------------------
hit_data <- test_clean %>%
  filter(stimulus_type == "Target") %>%
  mutate(hit = ifelse(response == "Old", 1, 0)) %>%
  group_by(participant_id, experiment) %>%
  summarise(hit_rate = mean(hit), .groups = "drop")

ggplot(hit_data, aes(x = hit_rate, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Accent") +
  labs(title = "Hit Rate Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 9. LDI & REC (SAFE COMPUTATION)
# ---------------------------------------------------------
safe_mean <- function(x){
  if(length(x) == 0) return(NA_real_)
  mean(x, na.rm = TRUE)
}

mst_metrics <- test_clean %>%
  group_by(participant_id, experiment) %>%
  summarise(
    p_old_target = safe_mean(stimulus_type == "Target" & response == "Old"),
    p_old_foil   = safe_mean(stimulus_type == "Foil" & response == "Old"),
    p_sim_lure   = safe_mean(stimulus_type == "Lure" & response == "Similar"),
    p_sim_foil   = safe_mean(stimulus_type == "Foil" & response == "Similar"),
    .groups = "drop"
  ) %>%
  mutate(
    REC = p_old_target - p_old_foil,
    LDI = p_sim_lure - p_sim_foil
  ) %>%
  filter(!is.na(REC), !is.na(LDI))

# REC
ggplot(mst_metrics, aes(x = REC, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "REC Distribution") +
  theme_minimal(base_size = 14)

# LDI
ggplot(mst_metrics, aes(x = LDI, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "LDI Distribution") +
  theme_minimal(base_size = 14)

cat("\n=========== VISUALISATION COMPLETE ===========\n")

```


# NORMALITY TESTING 
Normality tests are not performed on a single participant; they are applied to the distribution of values across participants. In this analysis, for each metric (reaction time, accuracy, hit rate, REC, LDI), we first computed a single summary value per participant (e.g., mean RT or LDI per condition), and then performed the Shapiro–Wilk test on the set of these participant-level values within each experiment. This is appropriate because the assumption of normality in statistical tests (like ANOVA or t-tests) applies to the sampling distribution across participants, not to individual trial data or a single participant’s observations.


```{r}
library(tidyverse)

cat("\n=========== NORMALITY TEST PIPELINE ===========\n")

# ---------------------------------------------------------
# HELPER FUNCTION
# ---------------------------------------------------------
run_normality <- function(values, label, exp){
  
  values <- values[!is.na(values)]
  
  cat("\n------------------------------\n")
  cat("Experiment:", exp, "\n")
  cat("Variable:", label, "\n")
  cat("Sample size:", length(values), "\n")
  
  if(length(values) < 3){
    cat("Not enough data\n")
    return(NULL)
  }
  
  print(shapiro.test(values))
  
  qqnorm(values, main = paste(label, "-", exp))
  qqline(values, col = "red")
}

# ---------------------------------------------------------
# LOOP OVER EXPERIMENTS
# ---------------------------------------------------------
for(exp in unique(test_clean$experiment)){
  
  cat("\n====================================\n")
  cat("PROCESSING:", exp, "\n")
  cat("====================================\n")
  
  task_exp <- task_clean %>% filter(experiment == exp)
  test_exp <- test_clean %>% filter(experiment == exp)
  
  # ---------------------------
  # RT
  # ---------------------------
  rt_summary <- task_exp %>%
    group_by(participant_id) %>%
    summarise(mean_rt = mean(rt), .groups = "drop")
  
  run_normality(rt_summary$mean_rt, "Reaction Time", exp)
  
  # ---------------------------
  # Accuracy
  # ---------------------------
  acc_summary <- test_exp %>%
    mutate(correct = case_when(
      stimulus_type == "Target" & response == "Old" ~ 1,
      stimulus_type == "Lure" & response == "Similar" ~ 1,
      stimulus_type == "Foil" & response == "New" ~ 1,
      TRUE ~ 0
    )) %>%
    group_by(participant_id) %>%
    summarise(accuracy = mean(correct), .groups = "drop")
  
  run_normality(acc_summary$accuracy, "Accuracy", exp)
  
  # ---------------------------
  # Hit Rate
  # ---------------------------
  hit_summary <- test_exp %>%
    filter(stimulus_type == "Target") %>%
    mutate(hit = ifelse(response == "Old", 1, 0)) %>%
    group_by(participant_id) %>%
    summarise(hit_rate = mean(hit), .groups = "drop")
  
  run_normality(hit_summary$hit_rate, "Hit Rate", exp)
  
  # ---------------------------
  # LDI & REC
  # ---------------------------
  mst_metrics <- test_exp %>%
    group_by(participant_id) %>%
    summarise(
      p_old_target = mean(stimulus_type == "Target" & response == "Old"),
      p_old_foil   = mean(stimulus_type == "Foil" & response == "Old"),
      p_sim_lure   = mean(stimulus_type == "Lure" & response == "Similar"),
      p_sim_foil   = mean(stimulus_type == "Foil" & response == "Similar"),
      .groups = "drop"
    ) %>%
    mutate(
      REC = p_old_target - p_old_foil,
      LDI = p_sim_lure - p_sim_foil
    ) %>%
    filter(!is.na(REC), !is.na(LDI))
  
  run_normality(mst_metrics$REC, "REC", exp)
  run_normality(mst_metrics$LDI, "LDI", exp)
}

cat("\n=========== NORMALITY TEST COMPLETE ===========\n")

```

# STATISTICAL METHODS 

# -----------------------------------------
# REACTION TIME ANALYSIS
# -----------------------------------------

```{r}

# -------------------------------
# 1. ADD BOUNDARY LABELS
# -------------------------------
task_clean <- task_clean %>%
  mutate(
    event_position = ((trial_number - 1) %% 7) + 1,
    boundary = case_when(
      event_position == 1 ~ "Post",
      event_position == 7 ~ "Pre",
      TRUE ~ "Non"
    )
  )

# -------------------------------
# 2. AGGREGATE RT PER PARTICIPANT
# -------------------------------
rt_summary <- task_clean %>%
  group_by(participant_id, experiment, boundary) %>%
  summarise(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop")

cat("\nRT Summary (first few rows):\n")
print(head(rt_summary))

# -------------------------------
# 3. GROUP-LEVEL SUMMARY (LIKE PAPER)
# -------------------------------
rt_group <- rt_summary %>%
  group_by(experiment, boundary) %>%
  summarise(
    mean_rt = mean(mean_rt),
    sd_rt = sd(mean_rt),
    n = n(),
    se = sd_rt / sqrt(n),
    .groups = "drop"
  )

cat("\nGroup-level RT summary:\n")
print(rt_group)

# -------------------------------
# 4. VISUALIZATION (MAIN PLOT)
# -------------------------------
ggplot(rt_group, aes(x = boundary, y = mean_rt, fill = boundary)) +
  geom_bar(stat = "identity", width = 0.6, alpha = 0.8) +
  geom_errorbar(
    aes(ymin = mean_rt - se, ymax = mean_rt + se),
    width = 0.2,
    size = 0.8
  ) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "Encoding Reaction Time by Boundary Position",
    x = "Boundary Condition",
    y = "Mean Reaction Time (seconds)"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# -------------------------------
# 5. PARTICIPANT-LEVEL VISUAL (OPTIONAL, MORE INFORMATIVE)
# -------------------------------
ggplot(rt_summary, aes(x = boundary, y = mean_rt, fill = boundary)) +
  geom_violin(alpha = 0.6) +
  geom_boxplot(width = 0.2, fill = "white", outlier.color = "red") +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "Participant-Level Reaction Time Distribution",
    x = "Boundary Condition",
    y = "Mean Reaction Time"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
  
```

Short answer: **yes, this is broadly in line with what you should expect**, but there are two subtle things to check before you fully trust it.

---

# 🔷 1. Does the pattern make sense?

From MST / Morse et al. logic:

* **Post-boundary → slower RT** (event model updating cost)
* **Pre-boundary → similar or slightly faster than baseline**
* **Non-boundary → baseline**

### Your plot shows:

| Experiment | Pattern                |
| ---------- | ---------------------- |
| both       | Post > Non ≈ Pre       |
| item_only  | very small differences |
| task_only  | Post clearly highest   |

👉 This is **exactly the qualitative pattern expected**:

* Strongest boundary effect in **task_only**
* Weakest in **item_only**
* Moderate in **both**

✔ This matches theory:

* Task boundaries disrupt processing more than item boundaries

---

# 🔷 2. One thing to double-check (important)

Your x-axis order is:

```id="check1"
Non, Post, Pre
```

But conceptually it should be:

```id="check2"
Pre → Non → Post
```

👉 Because:

* Pre is *before* boundary
* Post is *after* boundary

### Fix (for interpretation clarity):

```r
rt_group$boundary <- factor(
  rt_group$boundary,
  levels = c("Pre", "Non", "Post")
)
```

---

# 🔷 3. Are effect sizes reasonable?

From your plot:

* Differences ≈ **0.1–0.3 seconds**
* This is **realistic for RT data**

If you saw:

* 1+ second differences → suspicious
* identical bars → suspicious

👉 Your values look **plausible**

---

# 🔷 4. What would be “wrong” output?

Red flags (you do NOT have these):

* Pre > Post ❌
* No difference at all ❌
* Random pattern across experiments ❌

---

# 🔷 5. Interpretation you can use (report-ready)

You can state:

> Reaction times were highest for post-boundary items across experiments, indicating increased processing demands following event boundaries. This effect was strongest in the task-only condition and weakest in the item-only condition, consistent with the hypothesis that task boundaries induce greater cognitive disruption than item boundaries.

---

# 🔷 6. One improvement (optional but recommended)

Add error bars (you already computed SE):

👉 Without them, you can’t judge variability.

---

# 🔷 ✅ Final verdict

✔ Direction is correct
✔ Magnitude is reasonable
✔ Cross-experiment pattern is meaningful

👉 So yes — **this matches expectation**

# REPEATED MEASURES ANOVA 

The original analysis by Morse et al. used a two-way ANOVA treating boundary conditions (Pre, Non, Post) and trial type (Target/Lure) as independent factors. However, this approach implicitly assumes independence between observations across conditions. In this experiment, the same participants contribute data to all boundary conditions (Pre, Non, Post), meaning observations are not independent but repeated measures from the same individuals. Pre- and Post-boundary trials, in particular, arise from the same event transitions and reflect shared cognitive processes (event model updating). Ignoring this dependency violates ANOVA assumptions and can inflate Type I error. Therefore, a repeated-measures ANOVA is more appropriate, as it explicitly models within-subject variability and accounts for correlations between conditions. This preserves statistical validity while keeping all original metrics (RT, d′/REC, LDI) unchanged.

```{r}
cat("\n=========== REPEATED MEASURES ANOVA ANALYSIS ===========\n")

# ---------------------------------------------------------
# LOAD REQUIRED PACKAGES
# ---------------------------------------------------------
if (!require(afex)) {
  install.packages("afex")
  library(afex)
}
if (!require(emmeans)) {
  install.packages("emmeans")
  library(emmeans)
}

# ---------------------------------------------------------
# RUN ANOVA PER EXPERIMENT + STORE RESULTS
# ---------------------------------------------------------
anova_results <- list()
emm_results <- list()

for(exp in unique(rt_summary$experiment)){
  
  cat("\n============================\n")
  cat("Experiment:", exp, "\n")
  
  data_exp <- rt_summary %>% filter(experiment == exp)
  
  model <- aov_ez(
    id = "participant_id",
    dv = "mean_rt",
    data = data_exp,
    within = "boundary"
  )
  
  print(model)
  
  # Store model
  anova_results[[exp]] <- model
  
  # Get estimated marginal means
  emm <- emmeans(model, ~ boundary)
  emm_df <- as.data.frame(emm)
  emm_df$experiment <- exp
  
  emm_results[[exp]] <- emm_df
}

# Combine all experiments
emm_all <- bind_rows(emm_results)

# Order boundary correctly
emm_all$boundary <- factor(emm_all$boundary,
                           levels = c("Pre", "Non", "Post"))

# ---------------------------------------------------------
# PLOT: ANOVA-BASED (EMMEANS)
# ---------------------------------------------------------
ggplot(emm_all, aes(x = boundary, y = emmean, fill = boundary)) +
  geom_bar(stat = "identity", width = 0.6, alpha = 0.85) +
  geom_errorbar(
    aes(ymin = emmean - SE, ymax = emmean + SE),
    width = 0.2,
    size = 0.8
  ) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "ANOVA-Based Estimated Marginal Means (Reaction Time)",
    x = "Boundary Condition",
    y = "Estimated Mean RT"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

cat("\n=========== ANOVA PLOT COMPLETE ===========\n")
```

boundary effect is significant (p < .001)

### Post HOC Test using EMM
Post-hoc tests using EMM allow us to identify specific differences between conditions while correctly accounting for within-subject dependencies and interaction effects.

```{r}
# -----------------------------------------
# POST-HOC: REACTION TIME
# -----------------------------------------

cat("\n==== POST-HOC: REACTION TIME ====\n")

for(exp in unique(rt_summary$experiment)){
  
  cat("\nExperiment:", exp, "\n")
  
  data_exp <- rt_summary %>% filter(experiment == exp)
  
  model <- aov_ez(
    id = "participant_id",
    dv = "mean_rt",
    data = data_exp,
    within = "boundary"
  )
  
  emm <- emmeans(model, ~ boundary)
  
  # Pairwise comparisons
  pairwise <- pairs(emm, adjust = "bonferroni")
  print(pairwise)
}
```
No significant differences in reaction time were observed across boundary conditions in the item-only experiment (all p > .05).

Reaction times for Post-boundary items were significantly higher than both Non-boundary and Pre-boundary items (p < .001), while no difference was observed between Pre- and Non-boundary conditions.

Post-boundary reaction times were significantly higher than both Pre- and Non-boundary conditions (p < .001), with no difference between Pre and Non conditions.

Reaction time analyses revealed that event boundaries produced a significant processing cost in the both and task-only conditions, reflected by slower responses for Post-boundary items. However, no such effect was observed in the item-only condition, suggesting that perceptual shifts alone are insufficient to induce boundary-related processing costs. This pattern is consistent with Morse et al. (2023), who found that event boundaries only exert reliable cognitive effects when defined by a combination of perceptual and task-related changes, whereas perceptual shifts alone fail to produce strong boundary-related influences.

### One-Sample t-tests (Boundary vs Baseline)

```{r}
#--------------------------------------------
# STEP 0: CREATE COPIES (DO NOT MODIFY ORIGINALS)
#--------------------------------------------
task_copy <- task_all
test_copy <- test_clean


#--------------------------------------------
# STEP 1: CREATE BASE ID (FIX a/b ISSUE)
#--------------------------------------------
task_copy <- task_copy %>%
  mutate(base_id = gsub("[ab]\\.jpg$", "", image_name))

test_copy <- test_copy %>%
  mutate(base_id = gsub("[ab]\\.jpg$", "", image_name))


#--------------------------------------------
# STEP 2: CREATE BOUNDARY MAP FROM ENCODING
#--------------------------------------------
boundary_map <- task_copy %>%
  mutate(
    event_position = ((trial_number - 1) %% 7) + 1,
    boundary = case_when(
      event_position == 1 ~ "Post",
      event_position == 7 ~ "Pre",
      TRUE ~ "Non"
    )
  ) %>%
  select(participant_id, base_id, boundary) %>%
  group_by(participant_id, base_id) %>%
  summarise(boundary = first(boundary), .groups = "drop")


#--------------------------------------------
# STEP 3: ATTACH BOUNDARY TO TEST DATA
#--------------------------------------------
test_with_boundary <- test_copy %>%
  left_join(boundary_map, by = c("participant_id", "base_id"))


#--------------------------------------------
# HELPER FUNCTION
#--------------------------------------------
safe_div <- function(num, den){
  ifelse(den > 0, num / den, NA_real_)
}


#--------------------------------------------
# STEP 4: FOIL RATES (GLOBAL BASELINE)
#--------------------------------------------
foil_rates <- test_with_boundary %>%
  group_by(participant_id, experiment) %>%
  summarise(
    n_foil = sum(stimulus_type == "Foil"),
    
    fa_old_foil = sum(stimulus_type == "Foil" & response == "Old"),
    fa_sim_foil = sum(stimulus_type == "Foil" & response == "Similar"),
    
    p_old_foil = safe_div(fa_old_foil, n_foil),
    p_sim_foil = safe_div(fa_sim_foil, n_foil),
    
    .groups = "drop"
  )


#--------------------------------------------
# STEP 5: TARGET + LURE PER BOUNDARY
#--------------------------------------------
boundary_rates <- test_with_boundary %>%
  filter(!is.na(boundary)) %>%
  group_by(participant_id, experiment, boundary) %>%
  summarise(
    n_target = sum(stimulus_type == "Target"),
    n_lure   = sum(stimulus_type == "Lure"),
    
    hit_target = sum(stimulus_type == "Target" & response == "Old"),
    correct_lure = sum(stimulus_type == "Lure" & response == "Similar"),
    
    p_old_target = safe_div(hit_target, n_target),
    p_sim_lure   = safe_div(correct_lure, n_lure),
    
    .groups = "drop"
  )


#--------------------------------------------
# STEP 6: COMBINE → FINAL DATA
#--------------------------------------------
mst_boundary <- boundary_rates %>%
  left_join(foil_rates, by = c("participant_id", "experiment")) %>%
  mutate(
    REC = p_old_target - p_old_foil,
    LDI = p_sim_lure - p_sim_foil
  )


#--------------------------------------------
# STEP 7: VERIFY (CRITICAL CHECKS)
#--------------------------------------------
cat("\nBoundary counts:\n")
print(mst_boundary %>% count(boundary))

cat("\nLDI summary:\n")
print(summary(mst_boundary$LDI))

cat("\nREC summary:\n")
print(summary(mst_boundary$REC))

cat("\nCheck lure availability:\n")
print(
  mst_boundary %>%
    summarise(
      zero_lure = sum(n_lure == 0, na.rm = TRUE),
      total = n()
    )
)


#--------------------------------------------
# STEP 8: ONE-SAMPLE T-TESTS (LDI)
#--------------------------------------------
cat("\n==== ONE-SAMPLE TEST: LDI ====\n")

for(exp in unique(mst_boundary$experiment)){
  
  cat("\nExperiment:", exp, "\n")
  
  data_exp <- mst_boundary %>% filter(experiment == exp)
  
  pre  <- data_exp %>% filter(boundary == "Pre") %>% pull(LDI)
  non  <- data_exp %>% filter(boundary == "Non") %>% pull(LDI)
  post <- data_exp %>% filter(boundary == "Post") %>% pull(LDI)
  
  diff_pre  <- pre - non
  diff_post <- post - non
  
  diff_pre  <- diff_pre[!is.na(diff_pre)]
  diff_post <- diff_post[!is.na(diff_post)]
  
  if(length(diff_pre) > 1){
    cat("\nPre vs Non:\n")
    print(t.test(diff_pre, mu = 0))
  }
  
  if(length(diff_post) > 1){
    cat("\nPost vs Non:\n")
    print(t.test(diff_post, mu = 0))
  }
}


#--------------------------------------------
# STEP 9: ONE-SAMPLE T-TESTS (REC)
#--------------------------------------------
cat("\n==== ONE-SAMPLE TEST: REC ====\n")

for(exp in unique(mst_boundary$experiment)){
  
  cat("\nExperiment:", exp, "\n")
  
  data_exp <- mst_boundary %>% filter(experiment == exp)
  
  pre  <- data_exp %>% filter(boundary == "Pre") %>% pull(REC)
  non  <- data_exp %>% filter(boundary == "Non") %>% pull(REC)
  post <- data_exp %>% filter(boundary == "Post") %>% pull(REC)
  
  diff_pre  <- pre - non
  diff_post <- post - non
  
  diff_pre  <- diff_pre[!is.na(diff_pre)]
  diff_post <- diff_post[!is.na(diff_post)]
  
  if(length(diff_pre) > 1){
    cat("\nPre vs Non:\n")
    print(t.test(diff_pre, mu = 0))
  }
  
  if(length(diff_post) > 1){
    cat("\nPost vs Non:\n")
    print(t.test(diff_post, mu = 0))
  }
}


# VISUALIZATION CODE

#----------------------------------------------------------
# Mean LDI & REC by Boundary
#----------------------------------------------------------
library(ggplot2)

mst_long <- mst_boundary %>%
  select(participant_id, experiment, boundary, LDI, REC) %>%
  tidyr::pivot_longer(cols = c(LDI, REC), names_to = "metric", values_to = "value")

ggplot(mst_long, aes(x = boundary, y = value, fill = boundary)) +
  stat_summary(fun = mean, geom = "bar", alpha = 0.8) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_grid(metric ~ experiment) +
  labs(
    title = "Memory Performance by Boundary Condition",
    x = "Boundary",
    y = "Score"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
#----------------------------------------------------------
# Participant-Level Distribution
#----------------------------------------------------------
ggplot(mst_long, aes(x = boundary, y = value, fill = boundary)) +
  geom_violin(alpha = 0.5) +
  geom_boxplot(width = 0.2, fill = "white") +
  facet_grid(metric ~ experiment) +
  labs(
    title = "Distribution of LDI and REC Across Participants",
    x = "Boundary Condition",
    y = "Score"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
#----------------------------------------------------------
# Difference Scores
#----------------------------------------------------------
diff_data <- mst_boundary %>%
  tidyr::pivot_wider(names_from = boundary, values_from = c(LDI, REC)) %>%
  mutate(
    LDI_pre_diff  = LDI_Pre - LDI_Non,
    LDI_post_diff = LDI_Post - LDI_Non,
    REC_pre_diff  = REC_Pre - REC_Non,
    REC_post_diff = REC_Post - REC_Non
  ) %>%
  select(participant_id, experiment, starts_with("LDI"), starts_with("REC")) %>%
  tidyr::pivot_longer(
    cols = -c(participant_id, experiment),
    names_to = "condition",
    values_to = "value"
  )

ggplot(diff_data, aes(x = condition, y = value, fill = condition)) +
  stat_summary(fun = mean, geom = "bar") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  facet_wrap(~experiment) +
  labs(
    title = "Difference from Non-Boundary Baseline",
    x = "Condition",
    y = "Difference Score"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#---------------------------------------------------------------
# Quick Summary Plot
#--------------------------------------------------------------
mst_boundary %>%
  group_by(experiment, boundary) %>%
  summarise(
    mean_LDI = mean(LDI, na.rm = TRUE),
    mean_REC = mean(REC, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = boundary, y = mean_REC, group = experiment, color = experiment)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  facet_wrap(~experiment) +
  labs(
    title = "Recognition Performance Across Boundaries",
    y = "Mean REC"
  ) +
  theme_minimal(base_size = 14)
```
LDI Results (Pattern Separation)

One-sample t-tests compared boundary conditions against the Non-boundary baseline.

Across all three experiments (item_only, both, task_only), no significant differences in LDI were observed:

item_only
Pre vs Non: p = 0.396
Post vs Non: p = 0.595
both
Pre vs Non: p = 0.363
Post vs Non: p = 0.147
task_only
Pre vs Non: p = 0.317
Post vs Non: p = 0.249
Although LDI values were generally positive (Mean ≈ 0.33), indicating successful lure discrimination overall, event boundaries did not significantly modulate pattern separation.

REC Results (Recognition Memory)

Recognition performance showed condition-specific effects:

item_only
No significant differences (all p > 0.1)
both
Post vs Non: significant decrease
t(50) = -3.31, p = 0.0017
Indicates reduced recognition after boundaries
task_only
Pre vs Non: significant increase
t(52) = 2.15, p = 0.036
Indicates enhanced recognition before boundaries


These findings suggest a dissociation between memory processes:

Pattern separation (LDI) remains stable across event boundaries
Recognition (REC) is sensitive to boundary structure:
Pre-boundary enhancement (task_only)
Post-boundary impairment (both condition)

This partially aligns with the original study, where event boundaries influence memory encoding, but extends it by showing that effects are stronger for recognition than for pattern separation.

# Paired t-test (Pre vs Post)

The comparison between Pre- and Post-boundary conditions was conducted using a paired-samples t-test rather than an independent-samples t-test. This choice is justified because the same participants contributed data to both conditions, making the observations dependent (within-subject design).

In this experiment, each participant provides memory scores (LDI and REC) for Pre-boundary and Post-boundary items. These measurements are therefore not independent, as they are influenced by shared individual factors such as baseline memory ability, attention, and response tendencies. A paired t-test accounts for this dependency by analyzing within-subject differences, thereby reducing variability due to individual differences and increasing statistical power.

In contrast, an independent-samples t-test assumes that observations across groups are unrelated, which would violate the assumptions of the current experimental design and potentially lead to incorrect inferences.
```{r}
#---------------------------------------------------------
# STEP 1: RESHAPE DATA
#---------------------------------------------------------
library(tidyr)

mst_wide <- mst_boundary %>%
  select(participant_id, experiment, boundary, LDI, REC) %>%
  pivot_wider(
    names_from = boundary,
    values_from = c(LDI, REC)
  )
#---------------------------------------------------------
# STEP 2: PAIRED T-TEST (LDI)
#---------------------------------------------------------
cat("\n==== PAIRED TEST: LDI (Pre vs Post) ====\n")

for(exp in unique(mst_wide$experiment)){
  
  cat("\nExperiment:", exp, "\n")
  
  data_exp <- mst_wide %>% filter(experiment == exp)
  
  pre  <- data_exp$LDI_Pre
  post <- data_exp$LDI_Post
  
  # remove NA pairs
  valid <- !is.na(pre) & !is.na(post)
  
  if(sum(valid) > 1){
    print(t.test(pre[valid], post[valid], paired = TRUE))
  }
}
#---------------------------------------------------------
# STEP 3: PAIRED T-TEST (REC)
#---------------------------------------------------------
cat("\n==== PAIRED TEST: REC (Pre vs Post) ====\n")

for(exp in unique(mst_wide$experiment)){
  
  cat("\nExperiment:", exp, "\n")
  
  data_exp <- mst_wide %>% filter(experiment == exp)
  
  pre  <- data_exp$REC_Pre
  post <- data_exp$REC_Post
  
  valid <- !is.na(pre) & !is.na(post)
  
  if(sum(valid) > 1){
    print(t.test(pre[valid], post[valid], paired = TRUE))
  }
}
#---------------------------------------------------------
# VISUAL
#---------------------------------------------------------
mst_wide %>%
  pivot_longer(cols = c(LDI_Pre, LDI_Post), 
               names_to = "condition", values_to = "value") %>%
  ggplot(aes(x = condition, y = value, fill = condition)) +
  geom_boxplot() +
  facet_wrap(~experiment) +
  labs(title = "LDI: Pre vs Post Comparison") +
  theme_minimal()
```

To directly compare memory performance across event boundaries, paired-samples t-tests were conducted between Pre-boundary and Post-boundary conditions for both LDI and REC. This analysis captures within-subject differences in memory performance across boundary transitions.

🔹 Lure Discrimination Index (LDI)

Across all experimental conditions, no significant differences were observed between Pre- and Post-boundary items:

item_only: t(55) = -1.13, p = 0.262
both: t(50) = 0.61, p = 0.545
task_only: t(52) = -0.34, p = 0.738

👉 Although mean differences varied slightly across conditions, none reached statistical significance.

🧠 Interpretation

These results indicate that pattern separation (LDI) is not significantly influenced by event boundaries, suggesting that the ability to discriminate similar items remains stable across boundary transitions.

🔹 Recognition Memory (REC)

Recognition performance showed a condition-specific effect:

item_only:
t(55) = -1.78, p = 0.080 (marginal, not significant)
both:
t(50) = 2.94, p = 0.0049 ✔
Mean difference = +0.058 (Pre > Post)
task_only:
t(52) = 1.46, p = 0.150 (not significant)
🧠 Interpretation

A significant Pre > Post effect was observed in the both condition, indicating that recognition memory is stronger for items presented before an event boundary compared to those presented after.

No reliable differences were found in the item-only or task-only conditions, although the item-only condition showed a trend toward reduced performance post-boundary.

🔹 Overall Interpretation

These findings reveal a clear dissociation between memory processes:

LDI (pattern separation) → stable across boundaries
REC (recognition memory) → selectively affected by boundaries

Specifically:

Event boundaries appear to disrupt recognition for post-boundary items
Pre-boundary items benefit from enhanced encoding or consolidation
🔹 Comparison with Morse et al. (2023)

The present findings are partially consistent with Morse et al. (2023).

Similar to the original study, we observe reduced memory performance following event boundaries, reflected here as lower recognition for Post-boundary items.
Additionally, the enhancement of Pre-boundary memory aligns with the idea that boundaries trigger segmentation processes that strengthen encoding of preceding information.

However, unlike Morse et al., who reported more consistent boundary effects, the current results show that:

Effects are limited to the combined (“both”) condition
Pattern separation (LDI) remains unaffected, suggesting that boundary effects primarily influence recognition rather than fine-grained discrimination

