---
title: "Project Phase 2- Preliminary Analysis"
author: "Team Popcorn - Amritha, Ahana, Keerthana"
date: "05/3/2026"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
    latex_engine: xelatex
  
---
```{r}
knitr::opts_chunk$set(cache = FALSE)
```
# So we have three tasks in the MST_Data folder 
├── Both_item_task/
│   └── both_data/                # Data files for Experiment 1
├── item_only/
│   └── item_only_data/           # Data files for Experiment 2
├── task_only/
│   └── task_only_data/           # Data files for Experiment 3

# Dataset Description

The dataset used in this study is organized into three experimental conditions of the Mnemonic Similarity Task (MST): **Both Item + Task**, **Item-only**, and **Task-only**. Each condition is stored in a separate directory within the `MST_Data` folder.

Within each condition, the data is structured at the participant level. For every participant, there are two CSV files corresponding to the two phases of the experiment:

* a **task file**, representing the encoding (study) phase
* a **test file**, representing the retrieval (memory test) phase

The files follow a consistent naming convention of the form:
`<subjectID>_MST_<phase>_<date>_<timestamp>.csv`,
where the subject ID uniquely identifies each participant and the phase indicates whether the file corresponds to the encoding or test stage.

The task files primarily contain information related to stimulus presentation and encoding responses, including image paths, trial indices, and key responses recorded during the study phase.

The test files contain trial-level behavioral data used for analysis, including: 

stimulus identity (e.g., scene or object images)
stimulus condition (e.g., target, lure, foil — inferred from stimulus position/type)
participant responses (e.g., old, similar, new)
reaction times associated with each response

From these test-phase variables, key behavioral measures are computed:

LDI (Lure Discrimination Index), reflecting the ability to distinguish similar items
REC (Recognition Score), reflecting general recognition performance
Reaction Time (RT), capturing response latency

The dataset is structured such that each participant contributes multiple trials, enabling within-subject analysis of memory performance across different stimulus types.

Experiment	Condition:
1	Both (item + task boundary)
2	Item-only
3	Task-only
# Preprocessing 

```{r}

library(tidyverse)

base_path <- "../MST_Data"

clean_task_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  cat("Initial rows:", nrow(df), "\n")
  
  # -------------------------------
  # Extract participant ID
  # -------------------------------
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  # -------------------------------
  # Ensure required columns exist
  # -------------------------------
  required_cols <- c("image_path", "trials.thisN")
  
  missing_cols <- setdiff(required_cols, names(df))
  
  if(length(missing_cols) > 0){
    stop(paste("Missing columns:", paste(missing_cols, collapse=", ")))
  }
  
  # -------------------------------
  # Create RT columns if missing
  # -------------------------------
  if(!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if(!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  
  # -------------------------------
  # CLEAN
  # -------------------------------
  df_clean <- df %>%
    
    # remove non-trial rows
    filter(!is.na(trials.thisN)) %>%
    
    # remove empty image rows
    filter(!is.na(image_path), image_path != "") %>%
    
    # remove practice
    filter(!str_detect(image_path, "practice")) %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      
      # numeric safety
      rt_9 = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      rt_8 = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      
      # RT correction
      rt = case_when(
        !is.na(rt_9) ~ rt_9,
        !is.na(rt_8) ~ 3 + rt_8,
        TRUE ~ NA_real_
      ),
      
      image_name = basename(image_path)
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, rt)
  
  # -------------------------------
  # DEBUG PRINTS
  # -------------------------------
  cat("Rows after cleaning:", nrow(df_clean), "\n")
  cat("Unique images:", length(unique(df_clean$image_name)), "\n")
  cat("RT summary:\n")
  print(summary(df_clean$rt))
  
  return(df_clean)
}

# TEST PREPROCESSER
clean_test_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing TEST:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  df_clean <- df %>%
    
    filter(!is.na(trials.thisN)) %>%
    
    filter(!is.na(image_path), image_path != "") %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      image_name = basename(image_path),
      
      # classify stimulus
      stimulus_type = case_when(
        str_detect(tolower(image_path), "^foil") ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE ~ NA_character_
      ),
      
      # response mapping
      response = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE ~ NA_character_
      )
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, stimulus_type, response)
  
  # DEBUG
  cat("Rows:", nrow(df_clean), "\n")
  cat("Stimulus counts:\n")
  print(table(df_clean$stimulus_type))
  
  return(df_clean)
}

# LOAD ALL EXPEERIMENTS

load_experiment <- function(task_dir, test_dir, label) {
  
  cat("\n=============================\n")
  cat("LOADING EXPERIMENT:", label, "\n")
  
  task_files <- list.files(task_dir, pattern = "task.*\\.csv$", full.names = TRUE)
  test_files <- list.files(test_dir, pattern = "test.*\\.csv$", full.names = TRUE)
  
  cat("Task files:", length(task_files), "\n")
  cat("Test files:", length(test_files), "\n")
  
  task_data <- map_dfr(task_files, clean_task_file)
  test_data <- map_dfr(test_files, clean_test_file)
  
  task_data$experiment <- label
  test_data$experiment <- label
  
  return(list(task = task_data, test = test_data))
}

# RUN PREPROCESSING FOR ALL THREE EXPERIMENTS 

exp1 <- load_experiment(
  "../MST_Data/Both_item_task/both_data",
  "../MST_Data/Both_item_task/both_data",
  "both"
)

exp2 <- load_experiment(
  "../MST_Data/item_only/item_only_data",
  "../MST_Data/item_only/item_only_data",
  "item_only"
)

exp3 <- load_experiment(
  "../MST_Data/task_only/task_only_data",
  "../MST_Data/task_only/task_only_data",
  "task_only"
)

# Combine
task_all <- bind_rows(exp1$task, exp2$task, exp3$task)
test_all <- bind_rows(exp1$test, exp2$test, exp3$test)

cat("\nFINAL DATA SUMMARY\n")
cat("Total task rows:", nrow(task_all), "\n")
cat("Total test rows:", nrow(test_all), "\n")

# SANITY CHECK 
head(task_all)
summary(task_all$rt)
table(test_all$stimulus_type)
```

# VISUALISATION 
HOW TO USE THESE (IMPORTANT)
Check these before moving forward:
✅ Reaction Time
Right skew? → expected
Extreme outliers? → consider trimming/log transform
✅ Response Distribution
Balanced responses?
Too many “Old”? → bias issue
✅ Stimulus Types
Should roughly match:
✅ Accuracy / Hit Rate
Should be above chance (~0.5)
If not → data quality issue
✅ LDI / REC
Should be > 0 (as per MST theory)


```{r}
cat("\n================ VISUALIZATION PIPELINE ================\n")


# ---------------------------------------------------------
# 1. FIX STIMULUS CLASSIFICATION (IMPORTANT FIX)
# ---------------------------------------------------------
test_all_fixed <- test_all %>%
  mutate(
    stimulus_type = case_when(
      str_detect(tolower(image_path), "^foil") ~ "Foil",
      str_detect(image_name, "a\\.jpg$") ~ "Target",
      str_detect(image_name, "b\\.jpg$") ~ "Lure",
      TRUE ~ NA_character_
    )
  )

cat("\nStimulus distribution AFTER FIX:\n")
print(table(test_all_fixed$stimulus_type, useNA = "always"))

# ---------------------------------------------------------
# 2. CLEAN DATA (REMOVE INVALID)
# ---------------------------------------------------------
task_clean <- task_all %>%
  filter(!is.na(rt), is.finite(rt))

test_clean <- test_all_fixed %>%
  filter(!is.na(stimulus_type))

# ---------------------------------------------------------
# Custom Color Palette
# ---------------------------------------------------------
palette_main <- c(
  "Target" = "#2E86AB",
  "Lure"   = "#F18F01",
  "Foil"   = "#C73E1D"
)

palette_resp <- c(
  "Old" = "#1B998B",
  "Similar" = "#ED217C",
  "New" = "#2D3047"
)

# ---------------------------------------------------------
# 3. REACTION TIME DISTRIBUTION
# ---------------------------------------------------------
ggplot(task_clean, aes(x = rt, fill = experiment)) +
  geom_histogram(bins = 50, alpha = 0.6, color = "black") +
  geom_density(aes(color = experiment), linewidth = 1) +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = "Reaction Time Distribution", x = "RT", y = "Count") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 4. RT BOXPLOT
# ---------------------------------------------------------
ggplot(task_clean, aes(x = experiment, y = rt, fill = experiment)) +
  geom_boxplot(alpha = 0.7, outlier.color = "red") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "RT by Experiment") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 5. STIMULUS TYPE DISTRIBUTION (FIXED)
# ---------------------------------------------------------
ggplot(test_clean, aes(x = stimulus_type, fill = stimulus_type)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_main) +
  labs(title = "Stimulus Type Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 6. RESPONSE DISTRIBUTION
# ---------------------------------------------------------
ggplot(test_clean, aes(x = response, fill = response)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_resp) +
  labs(title = "Response Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 7. ACCURACY
# ---------------------------------------------------------
acc_data <- test_clean %>%
  mutate(correct = case_when(
    stimulus_type == "Target" & response == "Old" ~ 1,
    stimulus_type == "Lure" & response == "Similar" ~ 1,
    stimulus_type == "Foil" & response == "New" ~ 1,
    TRUE ~ 0
  )) %>%
  group_by(participant_id, experiment) %>%
  summarise(accuracy = mean(correct), .groups = "drop")

ggplot(acc_data, aes(x = accuracy, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Accuracy Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 8. HIT RATE
# ---------------------------------------------------------
hit_data <- test_clean %>%
  filter(stimulus_type == "Target") %>%
  mutate(hit = ifelse(response == "Old", 1, 0)) %>%
  group_by(participant_id, experiment) %>%
  summarise(hit_rate = mean(hit), .groups = "drop")

ggplot(hit_data, aes(x = hit_rate, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Accent") +
  labs(title = "Hit Rate Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 9. LDI & REC (SAFE COMPUTATION)
# ---------------------------------------------------------
safe_mean <- function(x){
  if(length(x) == 0) return(NA_real_)
  mean(x, na.rm = TRUE)
}

mst_metrics <- test_clean %>%
  group_by(participant_id, experiment) %>%
  summarise(
    p_old_target = safe_mean(stimulus_type == "Target" & response == "Old"),
    p_old_foil   = safe_mean(stimulus_type == "Foil" & response == "Old"),
    p_sim_lure   = safe_mean(stimulus_type == "Lure" & response == "Similar"),
    p_sim_foil   = safe_mean(stimulus_type == "Foil" & response == "Similar"),
    .groups = "drop"
  ) %>%
  mutate(
    REC = p_old_target - p_old_foil,
    LDI = p_sim_lure - p_sim_foil
  ) %>%
  filter(!is.na(REC), !is.na(LDI))

# REC
ggplot(mst_metrics, aes(x = REC, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "REC Distribution") +
  theme_minimal(base_size = 14)

# LDI
ggplot(mst_metrics, aes(x = LDI, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "LDI Distribution") +
  theme_minimal(base_size = 14)

cat("\n=========== VISUALISATION COMPLETE ===========\n")

```


# NORMALITY TESTING 
Normality tests are not performed on a single participant; they are applied to the distribution of values across participants. In this analysis, for each metric (reaction time, accuracy, hit rate, REC, LDI), we first computed a single summary value per participant (e.g., mean RT or LDI per condition), and then performed the Shapiro–Wilk test on the set of these participant-level values within each experiment. This is appropriate because the assumption of normality in statistical tests (like ANOVA or t-tests) applies to the sampling distribution across participants, not to individual trial data or a single participant’s observations.


```{r}
library(tidyverse)

cat("\n=========== NORMALITY TEST PIPELINE ===========\n")

# ---------------------------------------------------------
# HELPER FUNCTION
# ---------------------------------------------------------
run_normality <- function(values, label, exp){
  
  values <- values[!is.na(values)]
  
  cat("\n------------------------------\n")
  cat("Experiment:", exp, "\n")
  cat("Variable:", label, "\n")
  cat("Sample size:", length(values), "\n")
  
  if(length(values) < 3){
    cat("Not enough data\n")
    return(NULL)
  }
  
  print(shapiro.test(values))
  
  qqnorm(values, main = paste(label, "-", exp))
  qqline(values, col = "red")
}

# ---------------------------------------------------------
# LOOP OVER EXPERIMENTS
# ---------------------------------------------------------
for(exp in unique(test_clean$experiment)){
  
  cat("\n====================================\n")
  cat("PROCESSING:", exp, "\n")
  cat("====================================\n")
  
  task_exp <- task_clean %>% filter(experiment == exp)
  test_exp <- test_clean %>% filter(experiment == exp)
  
  # ---------------------------
  # RT
  # ---------------------------
  rt_summary <- task_exp %>%
    group_by(participant_id) %>%
    summarise(mean_rt = mean(rt), .groups = "drop")
  
  run_normality(rt_summary$mean_rt, "Reaction Time", exp)
  
  # ---------------------------
  # Accuracy
  # ---------------------------
  acc_summary <- test_exp %>%
    mutate(correct = case_when(
      stimulus_type == "Target" & response == "Old" ~ 1,
      stimulus_type == "Lure" & response == "Similar" ~ 1,
      stimulus_type == "Foil" & response == "New" ~ 1,
      TRUE ~ 0
    )) %>%
    group_by(participant_id) %>%
    summarise(accuracy = mean(correct), .groups = "drop")
  
  run_normality(acc_summary$accuracy, "Accuracy", exp)
  
  # ---------------------------
  # Hit Rate
  # ---------------------------
  hit_summary <- test_exp %>%
    filter(stimulus_type == "Target") %>%
    mutate(hit = ifelse(response == "Old", 1, 0)) %>%
    group_by(participant_id) %>%
    summarise(hit_rate = mean(hit), .groups = "drop")
  
  run_normality(hit_summary$hit_rate, "Hit Rate", exp)
  
  # ---------------------------
  # LDI & REC
  # ---------------------------
  mst_metrics <- test_exp %>%
    group_by(participant_id) %>%
    summarise(
      p_old_target = mean(stimulus_type == "Target" & response == "Old"),
      p_old_foil   = mean(stimulus_type == "Foil" & response == "Old"),
      p_sim_lure   = mean(stimulus_type == "Lure" & response == "Similar"),
      p_sim_foil   = mean(stimulus_type == "Foil" & response == "Similar"),
      .groups = "drop"
    ) %>%
    mutate(
      REC = p_old_target - p_old_foil,
      LDI = p_sim_lure - p_sim_foil
    ) %>%
    filter(!is.na(REC), !is.na(LDI))
  
  run_normality(mst_metrics$REC, "REC", exp)
  run_normality(mst_metrics$LDI, "LDI", exp)
}

cat("\n=========== NORMALITY TEST COMPLETE ===========\n")

```

# STATISTICAL METHODS 

# -----------------------------------------
# REACTION TIME ANALYSIS
# -----------------------------------------

```{r}

# -------------------------------
# 1. ADD BOUNDARY LABELS
# -------------------------------
task_clean <- task_clean %>%
  mutate(
    event_position = ((trial_number - 1) %% 7) + 1,
    boundary = case_when(
      event_position == 1 ~ "Post",
      event_position == 7 ~ "Pre",
      TRUE ~ "Non"
    )
  )

# -------------------------------
# 2. AGGREGATE RT PER PARTICIPANT
# -------------------------------
rt_summary <- task_clean %>%
  group_by(participant_id, experiment, boundary) %>%
  summarise(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop")

cat("\nRT Summary (first few rows):\n")
print(head(rt_summary))

# -------------------------------
# 3. GROUP-LEVEL SUMMARY (LIKE PAPER)
# -------------------------------
rt_group <- rt_summary %>%
  group_by(experiment, boundary) %>%
  summarise(
    mean_rt = mean(mean_rt),
    sd_rt = sd(mean_rt),
    n = n(),
    se = sd_rt / sqrt(n),
    .groups = "drop"
  )

cat("\nGroup-level RT summary:\n")
print(rt_group)

# -------------------------------
# 4. VISUALIZATION (MAIN PLOT)
# -------------------------------
ggplot(rt_group, aes(x = boundary, y = mean_rt, fill = boundary)) +
  geom_bar(stat = "identity", width = 0.6, alpha = 0.8) +
  geom_errorbar(
    aes(ymin = mean_rt - se, ymax = mean_rt + se),
    width = 0.2,
    size = 0.8
  ) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "Encoding Reaction Time by Boundary Position",
    x = "Boundary Condition",
    y = "Mean Reaction Time (seconds)"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# -------------------------------
# 5. PARTICIPANT-LEVEL VISUAL (OPTIONAL, MORE INFORMATIVE)
# -------------------------------
ggplot(rt_summary, aes(x = boundary, y = mean_rt, fill = boundary)) +
  geom_violin(alpha = 0.6) +
  geom_boxplot(width = 0.2, fill = "white", outlier.color = "red") +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "Participant-Level Reaction Time Distribution",
    x = "Boundary Condition",
    y = "Mean Reaction Time"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
  
```

Short answer: **yes, this is broadly in line with what you should expect**, but there are two subtle things to check before you fully trust it.

---

# 🔷 1. Does the pattern make sense?

From MST / Morse et al. logic:

* **Post-boundary → slower RT** (event model updating cost)
* **Pre-boundary → similar or slightly faster than baseline**
* **Non-boundary → baseline**

### Your plot shows:

| Experiment | Pattern                |
| ---------- | ---------------------- |
| both       | Post > Non ≈ Pre       |
| item_only  | very small differences |
| task_only  | Post clearly highest   |

👉 This is **exactly the qualitative pattern expected**:

* Strongest boundary effect in **task_only**
* Weakest in **item_only**
* Moderate in **both**

✔ This matches theory:

* Task boundaries disrupt processing more than item boundaries

---

# 🔷 2. One thing to double-check (important)

Your x-axis order is:

```id="check1"
Non, Post, Pre
```

But conceptually it should be:

```id="check2"
Pre → Non → Post
```

👉 Because:

* Pre is *before* boundary
* Post is *after* boundary

### Fix (for interpretation clarity):

```r
rt_group$boundary <- factor(
  rt_group$boundary,
  levels = c("Pre", "Non", "Post")
)
```

---

# 🔷 3. Are effect sizes reasonable?

From your plot:

* Differences ≈ **0.1–0.3 seconds**
* This is **realistic for RT data**

If you saw:

* 1+ second differences → suspicious
* identical bars → suspicious

👉 Your values look **plausible**

---

# 🔷 4. What would be “wrong” output?

Red flags (you do NOT have these):

* Pre > Post ❌
* No difference at all ❌
* Random pattern across experiments ❌

---

# 🔷 5. Interpretation you can use (report-ready)

You can state:

> Reaction times were highest for post-boundary items across experiments, indicating increased processing demands following event boundaries. This effect was strongest in the task-only condition and weakest in the item-only condition, consistent with the hypothesis that task boundaries induce greater cognitive disruption than item boundaries.

---

# 🔷 6. One improvement (optional but recommended)

Add error bars (you already computed SE):

👉 Without them, you can’t judge variability.

---

# 🔷 ✅ Final verdict

✔ Direction is correct
✔ Magnitude is reasonable
✔ Cross-experiment pattern is meaningful

👉 So yes — **this matches expectation**

# REPEATED MEASURES ANOVA 

The original analysis by Morse et al. used a two-way ANOVA treating boundary conditions (Pre, Non, Post) and trial type (Target/Lure) as independent factors. However, this approach implicitly assumes independence between observations across conditions. In this experiment, the same participants contribute data to all boundary conditions (Pre, Non, Post), meaning observations are not independent but repeated measures from the same individuals. Pre- and Post-boundary trials, in particular, arise from the same event transitions and reflect shared cognitive processes (event model updating). Ignoring this dependency violates ANOVA assumptions and can inflate Type I error. Therefore, a repeated-measures ANOVA is more appropriate, as it explicitly models within-subject variability and accounts for correlations between conditions. This preserves statistical validity while keeping all original metrics (RT, d′/REC, LDI) unchanged.

```{r}
cat("\n=========== REPEATED MEASURES ANOVA ANALYSIS ===========\n")

# ---------------------------------------------------------
# LOAD REQUIRED PACKAGES
# ---------------------------------------------------------
if (!require(afex)) {
  install.packages("afex")
  library(afex)
}
if (!require(emmeans)) {
  install.packages("emmeans")
  library(emmeans)
}

# ---------------------------------------------------------
# RUN ANOVA PER EXPERIMENT + STORE RESULTS
# ---------------------------------------------------------
anova_results <- list()
emm_results <- list()

for(exp in unique(rt_summary$experiment)){
  
  cat("\n============================\n")
  cat("Experiment:", exp, "\n")
  
  data_exp <- rt_summary %>% filter(experiment == exp)
  
  model <- aov_ez(
    id = "participant_id",
    dv = "mean_rt",
    data = data_exp,
    within = "boundary"
  )
  
  print(model)
  
  # Store model
  anova_results[[exp]] <- model
  
  # Get estimated marginal means
  emm <- emmeans(model, ~ boundary)
  emm_df <- as.data.frame(emm)
  emm_df$experiment <- exp
  
  emm_results[[exp]] <- emm_df
}

# Combine all experiments
emm_all <- bind_rows(emm_results)

# Order boundary correctly
emm_all$boundary <- factor(emm_all$boundary,
                           levels = c("Pre", "Non", "Post"))

# ---------------------------------------------------------
# PLOT: ANOVA-BASED (EMMEANS)
# ---------------------------------------------------------
ggplot(emm_all, aes(x = boundary, y = emmean, fill = boundary)) +
  geom_bar(stat = "identity", width = 0.6, alpha = 0.85) +
  geom_errorbar(
    aes(ymin = emmean - SE, ymax = emmean + SE),
    width = 0.2,
    size = 0.8
  ) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = c(
    "Pre" = "#2E86AB",
    "Non" = "#F6C85F",
    "Post" = "#D1495B"
  )) +
  labs(
    title = "ANOVA-Based Estimated Marginal Means (Reaction Time)",
    x = "Boundary Condition",
    y = "Estimated Mean RT"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

cat("\n=========== ANOVA PLOT COMPLETE ===========\n")
```