---
title: "Project Phase 2- Preliminary Analysis"
author: "Team Popcorn - Amritha, Ahana, Keerthana"
date: "05/3/2026"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
    latex_engine: xelatex
  
---
```{r}
knitr::opts_chunk$set(cache = FALSE)
```
# So we have three tasks in the MST_Data folder 
├── Both_item_task/
│   └── both_data/                # Data files for Experiment 1
├── item_only/
│   └── item_only_data/           # Data files for Experiment 2
├── task_only/
│   └── task_only_data/           # Data files for Experiment 3

# Dataset Description

The dataset used in this study is organized into three experimental conditions of the Mnemonic Similarity Task (MST): **Both Item + Task**, **Item-only**, and **Task-only**. Each condition is stored in a separate directory within the `MST_Data` folder.

Within each condition, the data is structured at the participant level. For every participant, there are two CSV files corresponding to the two phases of the experiment:

* a **task file**, representing the encoding (study) phase
* a **test file**, representing the retrieval (memory test) phase

The files follow a consistent naming convention of the form:
`<subjectID>_MST_<phase>_<date>_<timestamp>.csv`,
where the subject ID uniquely identifies each participant and the phase indicates whether the file corresponds to the encoding or test stage.

The task files primarily contain information related to stimulus presentation and encoding responses, including image paths, trial indices, and key responses recorded during the study phase.

The test files contain trial-level behavioral data used for analysis, including: 

stimulus identity (e.g., scene or object images)
stimulus condition (e.g., target, lure, foil — inferred from stimulus position/type)
participant responses (e.g., old, similar, new)
reaction times associated with each response

From these test-phase variables, key behavioral measures are computed:

LDI (Lure Discrimination Index), reflecting the ability to distinguish similar items
REC (Recognition Score), reflecting general recognition performance
Reaction Time (RT), capturing response latency

The dataset is structured such that each participant contributes multiple trials, enabling within-subject analysis of memory performance across different stimulus types.

Experiment	Condition:
1	Both (item + task boundary)
2	Item-only
3	Task-only
# Preprocessing 

```{r}

library(tidyverse)

base_path <- "../MST_Data"

clean_task_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  cat("Initial rows:", nrow(df), "\n")
  
  # -------------------------------
  # Extract participant ID
  # -------------------------------
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  # -------------------------------
  # Ensure required columns exist
  # -------------------------------
  required_cols <- c("image_path", "trials.thisN")
  
  missing_cols <- setdiff(required_cols, names(df))
  
  if(length(missing_cols) > 0){
    stop(paste("Missing columns:", paste(missing_cols, collapse=", ")))
  }
  
  # -------------------------------
  # Create RT columns if missing
  # -------------------------------
  if(!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if(!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  
  # -------------------------------
  # CLEAN
  # -------------------------------
  df_clean <- df %>%
    
    # remove non-trial rows
    filter(!is.na(trials.thisN)) %>%
    
    # remove empty image rows
    filter(!is.na(image_path), image_path != "") %>%
    
    # remove practice
    filter(!str_detect(image_path, "practice")) %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      
      # numeric safety
      rt_9 = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      rt_8 = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      
      # RT correction
      rt = case_when(
        !is.na(rt_9) ~ rt_9,
        !is.na(rt_8) ~ 3 + rt_8,
        TRUE ~ NA_real_
      ),
      
      image_name = basename(image_path)
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, rt)
  
  # -------------------------------
  # DEBUG PRINTS
  # -------------------------------
  cat("Rows after cleaning:", nrow(df_clean), "\n")
  cat("Unique images:", length(unique(df_clean$image_name)), "\n")
  cat("RT summary:\n")
  print(summary(df_clean$rt))
  
  return(df_clean)
}

# TEST PREPROCESSER
clean_test_file <- function(file_path) {
  
  cat("\n=============================\n")
  cat("Processing TEST:", basename(file_path), "\n")
  
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  
  participant_id <- str_extract(basename(file_path), "^\\d{5}")
  
  df_clean <- df %>%
    
    filter(!is.na(trials.thisN)) %>%
    
    filter(!is.na(image_path), image_path != "") %>%
    
    mutate(
      participant_id = participant_id,
      trial_number = trials.thisN + 1,
      image_name = basename(image_path),
      
      # classify stimulus
      stimulus_type = case_when(
        str_detect(tolower(image_path), "^foil") ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE ~ NA_character_
      ),
      
      # response mapping
      response = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE ~ NA_character_
      )
    ) %>%
    
    select(participant_id, trial_number, image_path, image_name, stimulus_type, response)
  
  # DEBUG
  cat("Rows:", nrow(df_clean), "\n")
  cat("Stimulus counts:\n")
  print(table(df_clean$stimulus_type))
  
  return(df_clean)
}

# LOAD ALL EXPEERIMENTS

load_experiment <- function(task_dir, test_dir, label) {
  
  cat("\n=============================\n")
  cat("LOADING EXPERIMENT:", label, "\n")
  
  task_files <- list.files(task_dir, pattern = "task.*\\.csv$", full.names = TRUE)
  test_files <- list.files(test_dir, pattern = "test.*\\.csv$", full.names = TRUE)
  
  cat("Task files:", length(task_files), "\n")
  cat("Test files:", length(test_files), "\n")
  
  task_data <- map_dfr(task_files, clean_task_file)
  test_data <- map_dfr(test_files, clean_test_file)
  
  task_data$experiment <- label
  test_data$experiment <- label
  
  return(list(task = task_data, test = test_data))
}

# RUN PREPROCESSING FOR ALL THREE EXPERIMENTS 

exp1 <- load_experiment(
  "../MST_Data/Both_item_task/both_data",
  "../MST_Data/Both_item_task/both_data",
  "both"
)

exp2 <- load_experiment(
  "../MST_Data/item_only/item_only_data",
  "../MST_Data/item_only/item_only_data",
  "item_only"
)

exp3 <- load_experiment(
  "../MST_Data/task_only/task_only_data",
  "../MST_Data/task_only/task_only_data",
  "task_only"
)

# Combine
task_all <- bind_rows(exp1$task, exp2$task, exp3$task)
test_all <- bind_rows(exp1$test, exp2$test, exp3$test)

cat("\nFINAL DATA SUMMARY\n")
cat("Total task rows:", nrow(task_all), "\n")
cat("Total test rows:", nrow(test_all), "\n")

# SANITY CHECK 
head(task_all)
summary(task_all$rt)
table(test_all$stimulus_type)
```

# VISUALISATION 
HOW TO USE THESE (IMPORTANT)
Check these before moving forward:
✅ Reaction Time
Right skew? → expected
Extreme outliers? → consider trimming/log transform
✅ Response Distribution
Balanced responses?
Too many “Old”? → bias issue
✅ Stimulus Types
Should roughly match:
✅ Accuracy / Hit Rate
Should be above chance (~0.5)
If not → data quality issue
✅ LDI / REC
Should be > 0 (as per MST theory)


```{r}
cat("\n================ VISUALIZATION PIPELINE ================\n")


# ---------------------------------------------------------
# 1. FIX STIMULUS CLASSIFICATION (IMPORTANT FIX)
# ---------------------------------------------------------
test_all_fixed <- test_all %>%
  mutate(
    stimulus_type = case_when(
      str_detect(tolower(image_path), "^foil") ~ "Foil",
      str_detect(image_name, "a\\.jpg$") ~ "Target",
      str_detect(image_name, "b\\.jpg$") ~ "Lure",
      TRUE ~ NA_character_
    )
  )

cat("\nStimulus distribution AFTER FIX:\n")
print(table(test_all_fixed$stimulus_type, useNA = "always"))

# ---------------------------------------------------------
# 2. CLEAN DATA (REMOVE INVALID)
# ---------------------------------------------------------
task_clean <- task_all %>%
  filter(!is.na(rt), is.finite(rt))

test_clean <- test_all_fixed %>%
  filter(!is.na(stimulus_type))

# ---------------------------------------------------------
# Custom Color Palette
# ---------------------------------------------------------
palette_main <- c(
  "Target" = "#2E86AB",
  "Lure"   = "#F18F01",
  "Foil"   = "#C73E1D"
)

palette_resp <- c(
  "Old" = "#1B998B",
  "Similar" = "#ED217C",
  "New" = "#2D3047"
)

# ---------------------------------------------------------
# 3. REACTION TIME DISTRIBUTION
# ---------------------------------------------------------
ggplot(task_clean, aes(x = rt, fill = experiment)) +
  geom_histogram(bins = 50, alpha = 0.6, color = "black") +
  geom_density(aes(color = experiment), linewidth = 1) +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(title = "Reaction Time Distribution", x = "RT", y = "Count") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 4. RT BOXPLOT
# ---------------------------------------------------------
ggplot(task_clean, aes(x = experiment, y = rt, fill = experiment)) +
  geom_boxplot(alpha = 0.7, outlier.color = "red") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "RT by Experiment") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 5. STIMULUS TYPE DISTRIBUTION (FIXED)
# ---------------------------------------------------------
ggplot(test_clean, aes(x = stimulus_type, fill = stimulus_type)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_main) +
  labs(title = "Stimulus Type Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 6. RESPONSE DISTRIBUTION
# ---------------------------------------------------------
ggplot(test_clean, aes(x = response, fill = response)) +
  geom_bar(alpha = 0.85) +
  facet_wrap(~experiment) +
  scale_fill_manual(values = palette_resp) +
  labs(title = "Response Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 7. ACCURACY
# ---------------------------------------------------------
acc_data <- test_clean %>%
  mutate(correct = case_when(
    stimulus_type == "Target" & response == "Old" ~ 1,
    stimulus_type == "Lure" & response == "Similar" ~ 1,
    stimulus_type == "Foil" & response == "New" ~ 1,
    TRUE ~ 0
  )) %>%
  group_by(participant_id, experiment) %>%
  summarise(accuracy = mean(correct), .groups = "drop")

ggplot(acc_data, aes(x = accuracy, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Accuracy Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 8. HIT RATE
# ---------------------------------------------------------
hit_data <- test_clean %>%
  filter(stimulus_type == "Target") %>%
  mutate(hit = ifelse(response == "Old", 1, 0)) %>%
  group_by(participant_id, experiment) %>%
  summarise(hit_rate = mean(hit), .groups = "drop")

ggplot(hit_data, aes(x = hit_rate, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Accent") +
  labs(title = "Hit Rate Distribution") +
  theme_minimal(base_size = 14)

# ---------------------------------------------------------
# 9. LDI & REC (SAFE COMPUTATION)
# ---------------------------------------------------------
safe_mean <- function(x){
  if(length(x) == 0) return(NA_real_)
  mean(x, na.rm = TRUE)
}

mst_metrics <- test_clean %>%
  group_by(participant_id, experiment) %>%
  summarise(
    p_old_target = safe_mean(stimulus_type == "Target" & response == "Old"),
    p_old_foil   = safe_mean(stimulus_type == "Foil" & response == "Old"),
    p_sim_lure   = safe_mean(stimulus_type == "Lure" & response == "Similar"),
    p_sim_foil   = safe_mean(stimulus_type == "Foil" & response == "Similar"),
    .groups = "drop"
  ) %>%
  mutate(
    REC = p_old_target - p_old_foil,
    LDI = p_sim_lure - p_sim_foil
  ) %>%
  filter(!is.na(REC), !is.na(LDI))

# REC
ggplot(mst_metrics, aes(x = REC, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "REC Distribution") +
  theme_minimal(base_size = 14)

# LDI
ggplot(mst_metrics, aes(x = LDI, fill = experiment)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black") +
  facet_wrap(~experiment) +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "LDI Distribution") +
  theme_minimal(base_size = 14)

cat("\n=========== VISUALISATION COMPLETE ===========\n")

```


```{r}
library(tidyverse)

cat("\n=========== NORMALITY TEST PIPELINE ===========\n")

# ---------------------------------------------------------
# HELPER FUNCTION
# ---------------------------------------------------------
run_normality <- function(values, label, exp){
  
  values <- values[!is.na(values)]
  
  cat("\n------------------------------\n")
  cat("Experiment:", exp, "\n")
  cat("Variable:", label, "\n")
  cat("Sample size:", length(values), "\n")
  
  if(length(values) < 3){
    cat("Not enough data\n")
    return(NULL)
  }
  
  print(shapiro.test(values))
  
  qqnorm(values, main = paste(label, "-", exp))
  qqline(values, col = "red")
}

# ---------------------------------------------------------
# LOOP OVER EXPERIMENTS
# ---------------------------------------------------------
for(exp in unique(test_clean$experiment)){
  
  cat("\n====================================\n")
  cat("PROCESSING:", exp, "\n")
  cat("====================================\n")
  
  task_exp <- task_clean %>% filter(experiment == exp)
  test_exp <- test_clean %>% filter(experiment == exp)
  
  # ---------------------------
  # RT
  # ---------------------------
  rt_summary <- task_exp %>%
    group_by(participant_id) %>%
    summarise(mean_rt = mean(rt), .groups = "drop")
  
  run_normality(rt_summary$mean_rt, "Reaction Time", exp)
  
  # ---------------------------
  # Accuracy
  # ---------------------------
  acc_summary <- test_exp %>%
    mutate(correct = case_when(
      stimulus_type == "Target" & response == "Old" ~ 1,
      stimulus_type == "Lure" & response == "Similar" ~ 1,
      stimulus_type == "Foil" & response == "New" ~ 1,
      TRUE ~ 0
    )) %>%
    group_by(participant_id) %>%
    summarise(accuracy = mean(correct), .groups = "drop")
  
  run_normality(acc_summary$accuracy, "Accuracy", exp)
  
  # ---------------------------
  # Hit Rate
  # ---------------------------
  hit_summary <- test_exp %>%
    filter(stimulus_type == "Target") %>%
    mutate(hit = ifelse(response == "Old", 1, 0)) %>%
    group_by(participant_id) %>%
    summarise(hit_rate = mean(hit), .groups = "drop")
  
  run_normality(hit_summary$hit_rate, "Hit Rate", exp)
  
  # ---------------------------
  # LDI & REC
  # ---------------------------
  mst_metrics <- test_exp %>%
    group_by(participant_id) %>%
    summarise(
      p_old_target = mean(stimulus_type == "Target" & response == "Old"),
      p_old_foil   = mean(stimulus_type == "Foil" & response == "Old"),
      p_sim_lure   = mean(stimulus_type == "Lure" & response == "Similar"),
      p_sim_foil   = mean(stimulus_type == "Foil" & response == "Similar"),
      .groups = "drop"
    ) %>%
    mutate(
      REC = p_old_target - p_old_foil,
      LDI = p_sim_lure - p_sim_foil
    ) %>%
    filter(!is.na(REC), !is.na(LDI))
  
  run_normality(mst_metrics$REC, "REC", exp)
  run_normality(mst_metrics$LDI, "LDI", exp)
}

cat("\n=========== NORMALITY TEST COMPLETE ===========\n")

```


