---
title: "Project Phase 1 Analysis"
author: "Team Popcorn - Amritha, Ahana, Keerthana"
date: "05/3/2026"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
    latex_engine: xelatex
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 3
    theme: flatly
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 8,
  fig.height = 5,
  fig.align  = "center",
  dpi        = 150
)

library(tidyverse)
library(afex)
library(lme4)
library(lmerTest)
library(knitr)
library(kableExtra)
library(patchwork)

theme_study <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title       = element_text(face = "bold", size = 13, hjust = 0.5),
      plot.subtitle    = element_text(size = 10, hjust = 0.5, color = "grey40"),
      axis.title       = element_text(size = 11),
      axis.text        = element_text(size = 10),
      strip.text       = element_text(face = "bold", size = 11),
      legend.position  = "none",
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(color = "grey92")
    )
}

bp_colors <- c(Non = "#4D9DE0", Pre = "#E15554", Post = "#3BB273")
```

---

# Helper Functions

```{r helper_functions}
# Shapiro-Wilk on a vector. Returns TRUE if normal.
is_normal <- function(x, label = "") {
  x <- x[!is.na(x)]
  if (length(x) < 3) {
    cat(sprintf("  %-40s  n too small\n", label))
    return(TRUE)
  }
  sw <- shapiro.test(x)
  normal <- sw$p.value >= 0.05
  cat(sprintf("  %-40s  W = %.4f  p = %.4f  ->  %s\n",
              label, sw$statistic, sw$p.value,
              ifelse(normal, "normal", "NON-NORMAL")))
  return(normal)
}

# Shapiro-Wilk kable summary table.
normality_table <- function(cells_df, caption_text = "Shapiro-Wilk Results") {
  results <- purrr::map_dfr(seq_len(nrow(cells_df)), function(i) {
    v <- cells_df$vals[[i]]
    v <- v[!is.na(v)]
    if (length(v) < 3) {
      return(tibble(Condition = cells_df$label[i], n = length(v),
                    W = NA, p = NA, Normal = "Too few"))
    }
    if (sd(v) == 0) {
      return(tibble(Condition = cells_df$label[i], n = length(v),
                    W = NA, p = NA, Normal = "Identical values"))
    }
    sw <- shapiro.test(v)
    tibble(
      Condition = cells_df$label[i],
      n         = length(v),
      W         = round(sw$statistic, 4),
      p         = round(sw$p.value,   4),
      Normal    = ifelse(sw$p.value >= 0.05, "Yes", "No")
    )
  })
  results %>%
    kable(caption = caption_text, align = "lrrrr") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE, font_size = 12)
}

# Descriptive statistics kable.
summary_table <- function(df, group_vars, dv, caption_text = "Descriptive Statistics") {
  df %>%
    group_by(across(all_of(group_vars))) %>%
    summarise(
      n          = sum(!is.na(.data[[dv]])),
      Median     = round(median(.data[[dv]], na.rm = TRUE), 3),
      Mean       = round(mean(.data[[dv]],   na.rm = TRUE), 3),
      SD         = round(sd(.data[[dv]],     na.rm = TRUE), 3),
      IQR        = round(IQR(.data[[dv]],    na.rm = TRUE), 3),
      .groups    = "drop"
    ) %>%
    kable(caption = caption_text, align = "llrrrrr") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE, font_size = 12)
}

# SAP 2.1: Aggregate RT to per-participant means per Boundary x Trial Type cell.
aggregate_rt <- function(df) {
  df %>%
    group_by(participant_id, boundary_position, stimulus_type) %>%
    summarise(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop")
}

# Safe wrapper around kruskal.test: skips and prints a message if fewer than
# 2 groups have observations, avoiding the "all in same group" crash.
safe_kruskal <- function(values, groups, label = "") {
  groups   <- droplevels(as.factor(groups))
  n_groups <- length(levels(groups)[tapply(values, groups,
                                           function(x) sum(!is.na(x))) > 0])
  if (n_groups < 2) {
    cat("  Skipped (fewer than 2 groups with data):", label, "\n")
    return(invisible(NULL))
  }
  print(kruskal.test(values ~ groups))
}

# Safe wrapper around pairwise.wilcox.test.
safe_pairwise_wilcox <- function(values, groups, label = "") {
  groups   <- droplevels(as.factor(groups))
  n_groups <- length(levels(groups)[tapply(values, groups,
                                           function(x) sum(!is.na(x))) > 0])
  if (n_groups < 2) {
    cat("  Skipped (fewer than 2 groups with data):", label, "\n")
    return(invisible(NULL))
  }
  print(pairwise.wilcox.test(values, groups,
                              p.adjust.method = "bonferroni", exact = FALSE))
}

# SAP 2.3/2.4: Two-way non-parametric RT analysis (Boundary x Trial Type).
# Aggregates RT to per-participant means first (SAP 2.1), then tests:
#   - Main effect of Boundary Position
#   - Main effect of Trial Type (comparing Target vs Lure mean RTs per participant,
#     collapsed across boundary, using Wilcoxon signed-rank since same participants)
#   - Boundary Position effect within Target items
#   - Boundary Position effect within Lure items
rt_test_nonparametric <- function(df, exp_label = "") {
  rt_agg <- aggregate_rt(df)

  cat("\n===", exp_label, ": Two-Way Non-Parametric RT Analysis ===\n")
  cat("N participants:", n_distinct(rt_agg$participant_id), "\n")

  cat("\n--- Kruskal-Wallis: Main Effect of Boundary Position (collapsed across Trial Type) ---\n")
  safe_kruskal(rt_agg$mean_rt, rt_agg$boundary_position, "boundary_position")

  cat("\n--- Main Effect of Trial Type: Wilcoxon signed-rank (paired, Target vs Lure per participant) ---\n")
  trial_type_wide <- rt_agg %>%
    mutate(stimulus_type = as.character(stimulus_type)) %>%
    group_by(participant_id, stimulus_type) %>%
    summarise(mean_rt = mean(mean_rt, na.rm = TRUE), .groups = "drop") %>%
    pivot_wider(names_from = stimulus_type, values_from = mean_rt)

  # Check both columns exist after pivot
  if (!all(c("Target", "Lure") %in% names(trial_type_wide))) {
    cat("  Skipped: stimulus_type does not contain both Target and Lure after aggregation.\n")
    cat("  Columns present:", paste(names(trial_type_wide), collapse = ", "), "\n")
  } else {
    trial_type_wide <- trial_type_wide %>%
      filter(!is.na(.data[["Target"]]), !is.na(.data[["Lure"]]))
    cat("Complete pairs:", nrow(trial_type_wide), "\n")
    if (nrow(trial_type_wide) >= 3) {
      print(wilcox.test(trial_type_wide$Target, trial_type_wide$Lure,
                        paired = TRUE, exact = FALSE))
    } else {
      cat("Too few complete pairs for Trial Type comparison.\n")
    }
  }

  cat("\n--- Kruskal-Wallis: Boundary Position within Target items ---\n")
  df_target <- rt_agg %>% filter(stimulus_type == "Target")
  safe_kruskal(df_target$mean_rt, df_target$boundary_position, "Target boundary")

  cat("\n--- Kruskal-Wallis: Boundary Position within Lure items ---\n")
  df_lure <- rt_agg %>% filter(stimulus_type == "Lure")
  safe_kruskal(df_lure$mean_rt, df_lure$boundary_position, "Lure boundary")

  cat("\n--- Pairwise Wilcoxon: Boundary Position collapsed across Trial Type (Bonferroni) ---\n")
  safe_pairwise_wilcox(rt_agg$mean_rt, rt_agg$boundary_position, "boundary_position")

  cat("\n--- Pairwise Wilcoxon: Boundary within Target items (Bonferroni) ---\n")
  safe_pairwise_wilcox(df_target$mean_rt, df_target$boundary_position, "Target boundary")

  cat("\n--- Pairwise Wilcoxon: Boundary within Lure items (Bonferroni) ---\n")
  safe_pairwise_wilcox(df_lure$mean_rt, df_lure$boundary_position, "Lure boundary")
}

# SAP 7.1: Normality-aware one-sample test on difference scores vs 0.
# Shapiro-Wilk first; t-test if normal, Wilcoxon signed-rank if not.
one_sample_test_adaptive <- function(x, label = "") {
  cat("\n---", label, "---\n")
  x <- x[!is.na(x)]
  if (length(x) < 3) { cat("Too few observations.\n"); return(invisible(NULL)) }
  sw <- shapiro.test(x)
  cat(sprintf("  Shapiro-Wilk: W = %.4f, p = %.4f -> %s\n",
              sw$statistic, sw$p.value,
              ifelse(sw$p.value >= 0.05, "normal -> one-sample t-test",
                     "NON-NORMAL -> Wilcoxon signed-rank")))
  if (sw$p.value >= 0.05) {
    print(t.test(x, mu = 0))
  } else {
    print(wilcox.test(x, mu = 0, exact = FALSE))
  }
}

# SAP 8: Paired Wilcoxon signed-rank for Pre vs Post (within-participant).
paired_wilcoxon <- function(df, dv, label = "") {
  cat("\n---", label, ": Paired Wilcoxon (Pre vs Post) ---\n")
  wide <- df %>%
    filter(boundary_position %in% c("Pre", "Post")) %>%
    select(participant_id, boundary_position, all_of(dv)) %>%
    pivot_wider(names_from = boundary_position, values_from = all_of(dv)) %>%
    filter(!is.na(Pre), !is.na(Post))
  cat("Complete pairs:", nrow(wide), "\n")
  print(wilcox.test(wide$Pre, wide$Post, paired = TRUE, exact = FALSE))
}

# SAP 9: Linear mixed-effects model.
# Memory ~ boundary_position + (1 | participant_id)
run_lme <- function(df, dv, label = "") {
  cat("\n===", label, ": Linear Mixed-Effects Model ===\n")
  cat("Formula:", dv, "~ boundary_position + (1 | participant_id)\n\n")
  complete_pids <- df %>%
    group_by(participant_id) %>%
    summarise(n_levels = n_distinct(boundary_position), .groups = "drop") %>%
    filter(n_levels == 3) %>% pull(participant_id)
  df_c <- df %>% filter(participant_id %in% complete_pids) %>% droplevels()
  cat("Participants included:", length(complete_pids), "\n\n")
  formula_str <- as.formula(paste(dv, "~ boundary_position + (1 | participant_id)"))
  m <- lmer(formula_str, data = df_c, REML = TRUE)
  print(summary(m))
  cat("\nAnova (Type III):\n")
  print(anova(m))
}

# SAP 10: Lure similarity bin analysis.
# Extracts bin from image name (assumes format: ..._binN_... or similar).
# Tests Boundary Position x Similarity Bin interaction via Kruskal-Wallis per bin
# and a combined pairwise table.
lure_bin_analysis <- function(test_df, task_df, exp_label = "") {
  cat("\n===", exp_label, ": Lure Similarity Bin Analysis ===\n\n")

  # Extract similarity bin from image name.
  # Tries common naming patterns: _1_, _2_, _3_ or bin1/bin2/bin3 or lure1/lure2/lure3.
  lure_data <- test_df %>%
    filter(stimulus_type == "Lure") %>%
    left_join(task_df %>% select(participant_id, image_name, boundary_position),
              by = c("participant_id", "image_name")) %>%
    filter(!is.na(boundary_position)) %>%
    mutate(
      sim_bin = case_when(
        str_detect(image_name, "_1[_\\.]|bin1|lure1|sim1|low")  ~ "Low",
        str_detect(image_name, "_2[_\\.]|bin2|lure2|sim2|med")  ~ "Medium",
        str_detect(image_name, "_3[_\\.]|bin3|lure3|sim3|high") ~ "High",
        TRUE ~ NA_character_
      ),
      lure_correct = (response_type == "Similar")
    ) %>%
    filter(!is.na(sim_bin))

  if (nrow(lure_data) == 0) {
    cat("No similarity bin information found in image names.\n")
    cat("Image name examples:\n")
    print(head(test_df$image_name[test_df$stimulus_type == "Lure"], 10))
    return(invisible(NULL))
  }

  cat("Lure trials with bin info:", nrow(lure_data), "\n")
  print(table(lure_data$sim_bin, lure_data$boundary_position))

  lure_agg <- lure_data %>%
    group_by(participant_id, boundary_position, sim_bin) %>%
    summarise(lure_CR = mean(lure_correct, na.rm = TRUE), .groups = "drop")

  cat("\n--- Kruskal-Wallis: Boundary Position within each Similarity Bin ---\n")
  for (b in unique(lure_agg$sim_bin)) {
    cat("\nBin:", b, "\n")
    sub <- lure_agg %>% filter(sim_bin == b)
    safe_kruskal(sub$lure_CR, sub$boundary_position, paste("Bin:", b))
  }

  cat("\n--- Kruskal-Wallis: Similarity Bin within each Boundary Position ---\n")
  for (bp in levels(lure_agg$boundary_position)) {
    cat("\nBoundary:", bp, "\n")
    sub <- lure_agg %>% filter(boundary_position == bp)
    safe_kruskal(sub$lure_CR, sub$sim_bin, paste("Boundary:", bp))
  }

  # Visualize
  sum_df <- lure_agg %>%
    group_by(boundary_position, sim_bin) %>%
    summarise(median_CR = median(lure_CR, na.rm = TRUE),
              iqr_CR    = IQR(lure_CR,    na.rm = TRUE),
              .groups   = "drop") %>%
    mutate(sim_bin = factor(sim_bin, levels = c("Low", "Medium", "High")))

  p <- ggplot(sum_df, aes(x = boundary_position, y = median_CR,
                           color = sim_bin, group = sim_bin)) +
    geom_line(linewidth = 1.1) +
    geom_point(size = 3.5) +
    geom_errorbar(aes(ymin = median_CR - iqr_CR / 2,
                      ymax = median_CR + iqr_CR / 2),
                  width = 0.15, linewidth = 0.7) +
    scale_color_manual(values = c(Low = "#4D9DE0", Medium = "#E15554",
                                   High = "#3BB273")) +
    labs(title = paste(exp_label, ": Lure CR by Boundary x Similarity Bin"),
         subtitle = "Error bars = +/- 1/2 IQR | Lines = similarity bins",
         x = "Boundary Position", y = "Lure Correct Rejection Rate",
         color = "Similarity Bin") +
    theme_study() + theme(legend.position = "right")
  print(p)
  return(invisible(lure_agg))
}

# Violin + boxplot + mean diamond.
violin_box_plot <- function(df, x_var, y_var, fill_var = x_var,
                            title = "", subtitle = "",
                            x_lab = x_var, y_lab = y_var,
                            facet_var = NULL, colors = bp_colors) {
  p <- ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]],
                      fill = .data[[fill_var]])) +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30",
                 outlier.size = 1.5, outlier.alpha = 0.5) +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(values = colors) +
    labs(title = title, subtitle = subtitle, x = x_lab, y = y_lab) +
    theme_study()
  if (!is.null(facet_var))
    p <- p + facet_wrap(as.formula(paste("~", facet_var)))
  return(p)
}

# Bar chart with +/- 1 SE.
bar_se_plot <- function(df, x_var, y_var, title = "", subtitle = "",
                        x_lab = x_var, y_lab = y_var,
                        facet_var = NULL, colors = bp_colors) {
  sum_df <- df %>%
    group_by(across(all_of(c(x_var, facet_var)))) %>%
    summarise(mean_val = mean(.data[[y_var]], na.rm = TRUE),
              se_val   = sd(.data[[y_var]],   na.rm = TRUE) / sqrt(n()),
              .groups  = "drop")
  p <- ggplot(sum_df, aes(x = .data[[x_var]], y = mean_val,
                           fill = .data[[x_var]])) +
    geom_col(width = 0.6, alpha = 0.85, color = "white") +
    geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val),
                  width = 0.2, color = "grey30", linewidth = 0.7) +
    scale_fill_manual(values = colors) +
    labs(title = title, subtitle = subtitle, x = x_lab, y = y_lab) +
    theme_study()
  if (!is.null(facet_var))
    p <- p + facet_wrap(as.formula(paste("~", facet_var)))
  return(p)
}

# Line plot of medians across boundary positions.
boundary_line_plot <- function(df, x_var, y_var, group_var,
                               title = "", subtitle = "",
                               x_lab = x_var, y_lab = y_var,
                               colors = c("#E15554", "#3BB273")) {
  sum_df <- df %>%
    group_by(across(all_of(c(x_var, group_var)))) %>%
    summarise(median_val = median(.data[[y_var]], na.rm = TRUE),
              iqr_val    = IQR(.data[[y_var]],    na.rm = TRUE),
              .groups    = "drop")
  ggplot(sum_df, aes(x = .data[[x_var]], y = median_val,
                     color = .data[[group_var]], group = .data[[group_var]])) +
    geom_line(linewidth = 1.1) +
    geom_point(size = 3.5) +
    geom_errorbar(aes(ymin = median_val - iqr_val / 2,
                      ymax = median_val + iqr_val / 2),
                  width = 0.15, linewidth = 0.7) +
    scale_color_manual(values = colors) +
    labs(title = title, subtitle = subtitle,
         x = x_lab, y = y_lab, color = group_var) +
    theme_study() + theme(legend.position = "right")
}

# Q-Q plot.
qq_plot <- function(x, label = "") {
  tibble(vals = x) %>%
    ggplot(aes(sample = vals)) +
    stat_qq(color = "#4D9DE0", alpha = 0.7, size = 1.5) +
    stat_qq_line(color = "#E15554", linewidth = 0.9) +
    labs(title = paste("Q-Q:", label),
         subtitle = "Points close to line = normal",
         x = "Theoretical Quantiles", y = "Sample Quantiles") +
    theme_study()
}

# Difference score violin plot (Pre-Non and Post-Non).
diff_score_plot <- function(diff_df, title = "") {
  diff_df %>%
    select(participant_id, lure_pre_diff, lure_post_diff,
           target_pre_diff, target_post_diff) %>%
    pivot_longer(-participant_id, names_to = "contrast", values_to = "diff") %>%
    mutate(
      Measure   = ifelse(str_detect(contrast, "lure"), "Lure CR", "Target Hit"),
      Condition = ifelse(str_detect(contrast, "pre"), "Pre - Non", "Post - Non")
    ) %>%
    ggplot(aes(x = Condition, y = diff, fill = Condition)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30") +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(values = c("Pre - Non" = "#E15554", "Post - Non" = "#3BB273")) +
    facet_wrap(~ Measure) +
    labs(title = title, subtitle = "Dashed line = 0 (no difference from baseline)",
         x = "Contrast", y = "Difference in Proportion Correct") +
    theme_study()
}

# REC / LDI violin plot.
rec_ldi_plot <- function(metrics_df, rec_col, ldi_col, title = "") {
  metrics_df %>%
    pivot_longer(cols = c(all_of(rec_col), all_of(ldi_col)),
                 names_to = "Metric", values_to = "Value") %>%
    mutate(Metric = recode(Metric, !!rec_col := "REC", !!ldi_col := "LDI")) %>%
    ggplot(aes(x = Metric, y = Value, fill = Metric)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30",
                 outlier.size = 1.5, outlier.alpha = 0.5) +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(values = c(REC = "#4D9DE0", LDI = "#E15554")) +
    labs(title = title, subtitle = "Dashed line = chance (0)",
         x = "Metric", y = "Score") +
    theme_study()
}

# Friedman test + pairwise Wilcoxon for repeated measures non-parametric.
friedman_posthoc <- function(df, dv, pid_var = "participant_id",
                              within_var = "boundary_position", label = "") {
  cat("\n---", label, ": Friedman Test ---\n")

  # Keep only participants with all 3 boundary positions
  complete_pids <- df %>%
    group_by(.data[[pid_var]]) %>%
    summarise(n_levels = n_distinct(.data[[within_var]]), .groups = "drop") %>%
    filter(n_levels == 3) %>%
    pull(.data[[pid_var]])

  df_complete <- df %>%
    filter(.data[[pid_var]] %in% complete_pids) %>%
    droplevels()

  n_complete   <- length(complete_pids)
  n_dropped    <- n_distinct(df[[pid_var]]) - n_complete
  cat("Participants included:", n_complete,
      "| Dropped (incomplete):", n_dropped, "\n\n")

  if (n_complete < 3) {
    cat("Too few complete participants to run Friedman test.\n")
    return(invisible(NULL))
  }

  # Build wide matrix for friedman.test
  wide <- df_complete %>%
    select(all_of(c(pid_var, within_var, dv))) %>%
    pivot_wider(names_from  = all_of(within_var),
                values_from = all_of(dv),
                values_fn   = mean) %>%
    select(-all_of(pid_var))

  mat <- as.matrix(wide)

  ft <- friedman.test(mat)
  print(ft)

  cat("\nPairwise Wilcoxon signed-rank (Bonferroni corrected):\n")
  long <- df_complete %>%
    select(all_of(c(pid_var, within_var, dv)))

  levels_bp <- levels(df_complete[[within_var]])
  pairs <- combn(levels_bp, 2, simplify = FALSE)
  results <- map_dfr(pairs, function(pair) {
    g1 <- pair[1]; g2 <- pair[2]
    x1 <- long[[dv]][long[[within_var]] == g1]
    x2 <- long[[dv]][long[[within_var]] == g2]
    wt <- wilcox.test(x1, x2, paired = FALSE, exact = FALSE)
    tibble(
      Comparison = paste(g1, "vs", g2),
      W          = round(wt$statistic, 2),
      p_raw      = round(wt$p.value,   4)
    )
  })

  n_pairs <- nrow(results)
  results <- results %>%
    mutate(p_bonferroni = round(p.adjust(p_raw, method = "bonferroni"), 4),
           Significant  = ifelse(p_bonferroni < 0.05, "Yes", "No"))

  print(
    kable(results,
          caption = paste("Pairwise Wilcoxon -", label, "(Bonferroni)"),
          align   = "lrrrc") %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE, font_size = 12)
  )

  return(invisible(df_complete))
}
```

---

# Experiment 1: Both Item and Task

## 1.1 Load and Clean Task Data

```{r exp1_task_load}
task_files <- list.files(
  "Both_item_task/both_data", pattern = "_MST_task_.*\\.csv$", full.names = TRUE
)
cat("Task files found:", length(task_files), "\n")

load_exp1_task <- function(file_path) {
  df  <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  pid <- substr(basename(file_path), 1, 5)
  if (!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if (!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id    = pid,
      image_name        = basename(image_path),
      trial_number      = trials.thisN + 1,
      rt9               = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      rt8               = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      rt = case_when(
        !is.na(rt9) ~ rt9 * 1000,
        !is.na(rt8) ~ (3 + rt8) * 1000,
        TRUE        ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post"))
    )
}

df_both_task <- map_dfr(task_files, load_exp1_task)
cat("Unique participants:", n_distinct(df_both_task$participant_id), "\n")
```

```{r exp1_task_count_table}
df_both_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 1 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.2 Load and Clean Test Data

```{r exp1_test_load}
test_files <- list.files(
  "Both_item_task/both_data", pattern = "_MST_test_.*\\.csv$", full.names = TRUE
)
cat("Test files found:", length(test_files), "\n")

load_exp1_test <- function(file_path) {
  df <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id = as.character(participant),
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_both_test <- map_dfr(test_files, load_exp1_test)
cat("Unique participants:", n_distinct(df_both_test$participant_id), "\n")
cat("Stimulus type counts:\n")
print(table(df_both_test$stimulus_type, useNA = "always"))
```

```{r exp1_pid_diagnostic}
# PID alignment check
task_pids <- sort(unique(df_both_task$participant_id))
test_pids <- sort(unique(df_both_test$participant_id))
cat("Task PIDs:\n"); print(task_pids)
cat("\nTest PIDs:\n"); print(test_pids)
cat("\nIn task but not test:", setdiff(task_pids, test_pids), "\n")
cat("In test but not task:", setdiff(test_pids, task_pids), "\n")
```

```{r exp1_test_response_table}
df_both_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 1 Test: Response Counts by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.3 Join Stimulus Type to Task Data

```{r exp1_join}
# Normalize PIDs to numeric string to ensure join succeeds
df_both_task <- df_both_task %>%
  mutate(participant_id = as.character(as.integer(participant_id)))

df_both_test <- df_both_test %>%
  mutate(participant_id = as.character(as.integer(participant_id)))

df_both_task_labeled <- df_both_task %>%
  left_join(
    df_both_test %>%
      filter(stimulus_type %in% c("Target", "Lure")) %>%
      select(participant_id, image_name, stimulus_type) %>%
      distinct(),
    by = c("participant_id", "image_name")
  ) %>%
  filter(!is.na(stimulus_type), !is.na(rt)) %>%
  mutate(
    stimulus_type     = factor(stimulus_type),
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    participant_id    = factor(participant_id)
  )

cat("Rows after join:", nrow(df_both_task_labeled), "\n")
cat("Participants after join:", n_distinct(df_both_task_labeled$participant_id), "\n")
```

```{r exp1_cell_count_table}
df_both_task_labeled %>%
  count(boundary_position, stimulus_type) %>%
  pivot_wider(names_from = stimulus_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 1: RT Analysis Cell Counts") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.4 Normality Check

```{r exp1_rt_normality_table}
cells_rt_both <- df_both_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_both, "Exp 1: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp1_rt_qq, fig.height=8}
wrap_plots(
  pmap(list(cells_rt_both$vals, cells_rt_both$label),
       function(v, lbl) qq_plot(v[!is.na(v)], lbl)),
  ncol = 2
)
```

**Normality does not hold -> proceeding with non-parametric tests throughout.**

## 1.5 Non-Parametric RT Test

```{r exp1_rt_test}
rt_test_nonparametric(df_both_task_labeled, "Experiment 1")
```

## 1.6 RT Descriptive Statistics and Plots

```{r exp1_rt_desc}
summary_table(df_both_task_labeled, c("boundary_position", "stimulus_type"),
              "rt", "Exp 1: Encoding RT (ms) - Median and IQR")
```

```{r exp1_rt_violin}
violin_box_plot(df_both_task_labeled,
                x_var = "boundary_position", y_var = "rt",
                facet_var = "stimulus_type",
                title = "Exp 1: Encoding RT by Boundary Condition",
                subtitle = "Diamond = mean | Box = IQR | Violin = distribution",
                x_lab = "Boundary Position", y_lab = "RT (ms)")
```

```{r exp1_rt_bar}
bar_se_plot(df_both_task_labeled,
            x_var = "boundary_position", y_var = "rt",
            facet_var = "stimulus_type",
            title = "Exp 1: Mean Encoding RT",
            subtitle = "Error bars = +/- 1 SE",
            x_lab = "Boundary Position", y_lab = "Mean RT (ms)")
```

## 1.7 REC and LDI

```{r exp1_rec_ldi}
mst_metrics_both <- df_both_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target = mean(stimulus_type == "Target" & response_type == "Old",     na.rm = TRUE),
    p_old_foil   = mean(stimulus_type == "Foil"   & response_type == "Old",     na.rm = TRUE),
    p_sim_lure   = mean(stimulus_type == "Lure"   & response_type == "Similar", na.rm = TRUE),
    p_sim_foil   = mean(stimulus_type == "Foil"   & response_type == "Similar", na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(REC = p_old_target - p_old_foil,
         LDI = p_sim_lure   - p_sim_foil)

mst_metrics_both %>%
  select(participant_id, REC, LDI) %>%
  mutate(across(c(REC, LDI), ~ round(.x, 3))) %>%
  kable(caption = "Exp 1: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

mst_metrics_both %>%
  summarise(
    REC_median = round(median(REC), 3), REC_IQR = round(IQR(REC), 3),
    LDI_median = round(median(LDI), 3), LDI_IQR = round(IQR(LDI), 3)
  ) %>%
  kable(caption = "Exp 1: Group REC and LDI Summary (Median / IQR)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

rec_ldi_plot(mst_metrics_both, "REC", "LDI",
             "Exp 1: Distribution of REC and LDI Scores")
```

## 1.8 Memory Accuracy: Compute and Descriptives

```{r exp1_accuracy}
boundary_perf_both <- df_both_test %>%
  left_join(
    df_both_task %>% select(participant_id, image_name, boundary_position),
    by = c("participant_id", "image_name")
  ) %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct      = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit        = (stimulus_type == "Target" & response_type == "Old")
  ) %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  ) %>%
  filter(!is.na(boundary_position))

cat("Participants in accuracy data:", n_distinct(boundary_perf_both$participant_id), "\n")
```

```{r exp1_normality_accuracy}
cells_lure_both <- boundary_perf_both %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR", boundary_position, sep = " | "))

cells_target_both <- boundary_perf_both %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit", boundary_position, sep = " | "))

normality_table(cells_lure_both,   "Exp 1: Shapiro-Wilk - Lure CR by Boundary")
normality_table(cells_target_both, "Exp 1: Shapiro-Wilk - Target Hit by Boundary")
```

```{r exp1_accuracy_desc}
summary_table(boundary_perf_both, "boundary_position", "lure_CR",
              "Exp 1: Lure Correct Rejection Rate (Median / IQR)")
summary_table(boundary_perf_both, "boundary_position", "target_hit",
              "Exp 1: Target Hit Rate (Median / IQR)")
```

## 1.9 Memory Accuracy: Plots

```{r exp1_accuracy_violin}
boundary_perf_both %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  violin_box_plot("boundary_position", "acc", facet_var = "measure",
                  title = "Exp 1: Memory Accuracy by Boundary Condition",
                  subtitle = "Diamond = mean",
                  x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

```{r exp1_accuracy_line}
boundary_perf_both %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  boundary_line_plot("boundary_position", "acc", "measure",
                     title = "Exp 1: Memory Accuracy Trend",
                     subtitle = "Error bars = +/- 1/2 IQR",
                     x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

## 1.10 Friedman Test (Non-Parametric Repeated Measures)

```{r exp1_friedman}
friedman_posthoc(boundary_perf_both, "lure_CR",    label = "Exp 1: Lure CR")
friedman_posthoc(boundary_perf_both, "target_hit", label = "Exp 1: Target Hit")
```

## 1.11 One-Sample Tests: Boundary vs Baseline (Wilcoxon Signed-Rank)

```{r exp1_one_sample}
perf_diff_both <- boundary_perf_both %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit)) %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

#one_sample_test_adaptive(perf_diff_both$lure_pre_diff,    "lure Pre - Non (Exp1)")
#one_sample_test_adaptive(perf_diff_both$lure_post_diff,   "lure Post - Non (Exp1)")
#one_sample_test_adaptive(perf_diff_both$target_pre_diff,  "target Pre - Non (Exp1)")
#one_sample_test_adaptive(perf_diff_both$target_post_diff, "target Post - Non (Exp1)")
```

```{r exp1_diff_plot}
diff_score_plot(perf_diff_both,
                "Exp 1: Difference Scores Relative to Non-Boundary Baseline")
```

## 1.12 Pre vs Post: Paired Wilcoxon Signed-Rank (SAP Section 8)

```{r exp1_paired}
paired_wilcoxon(boundary_perf_both, "lure_CR",    "Exp 1 Lure CR")
paired_wilcoxon(boundary_perf_both, "target_hit", "Exp 1 Target Hit")
```

## 1.13 Linear Mixed-Effects Model (SAP Section 9)

```{r exp1_lme}
run_lme(boundary_perf_both, "lure_CR",    "Exp 1 Lure CR")
run_lme(boundary_perf_both, "target_hit", "Exp 1 Target Hit")
```

## 1.14 Lure Similarity Bin Analysis (SAP Section 10)

```{r exp1_lure_bin}
lure_bin_analysis(df_both_test, df_both_task, "Exp 1")
```

---

# Experiment 2: Item Only

## 2.1 Load and Clean Task Data

```{r exp2_task_load}
item_task_files <- list.files(
  "item_only/item_only_data", pattern = "_MST_task_.*\\.csv$", full.names = TRUE
)
cat("Item task files:", length(item_task_files), "\n")

load_exp2_task <- function(file_path) {
  df  <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  pid <- substr(basename(file_path), 1, 5)
  if (!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if (!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id    = pid,
      image_name        = basename(image_path),
      trial_number      = trials.thisN + 1,
      rt9               = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      rt8               = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      rt = case_when(
        !is.na(rt9) ~ rt9 * 1000,
        !is.na(rt8) ~ (3 + rt8) * 1000,
        TRUE        ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post"))
    )
}

df_item_task <- map_dfr(item_task_files, load_exp2_task)
cat("Unique participants:", n_distinct(df_item_task$participant_id), "\n")
```

```{r exp2_task_count_table}
df_item_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 2 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 2.2 Load and Clean Test Data

```{r exp2_test_load}
item_test_files <- list.files(
  "item_only/item_only_data", pattern = "_MST_test_.*\\.csv$", full.names = TRUE
)
cat("Item test files:", length(item_test_files), "\n")

load_exp2_test <- function(file_path) {
  df <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id = as.character(participant),
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_item_test <- map_dfr(item_test_files, load_exp2_test)
cat("Unique participants:", n_distinct(df_item_test$participant_id), "\n")
```

```{r exp2_pid_diagnostic}
df_item_task  <- df_item_task  %>% mutate(participant_id = as.character(as.integer(participant_id)))
df_item_test  <- df_item_test  %>% mutate(participant_id = as.character(as.integer(participant_id)))
task_pids2 <- sort(unique(df_item_task$participant_id))
test_pids2 <- sort(unique(df_item_test$participant_id))
cat("In task but not test:", setdiff(task_pids2, test_pids2), "\n")
cat("In test but not task:", setdiff(test_pids2, task_pids2), "\n")
```

```{r exp2_test_response_table}
df_item_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 2 Test: Response Counts by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 2.3 Join, Normality Check, and RT Test

```{r exp2_join}
df_item_task_labeled <- df_item_task %>%
  left_join(
    df_item_test %>%
      filter(stimulus_type %in% c("Target", "Lure")) %>%
      select(participant_id, image_name, stimulus_type) %>%
      distinct(),
    by = c("participant_id", "image_name")
  ) %>%
  filter(!is.na(stimulus_type), !is.na(rt)) %>%
  mutate(
    stimulus_type     = factor(stimulus_type),
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    participant_id    = factor(participant_id)
  )

cat("Rows after join:", nrow(df_item_task_labeled), "\n")
cat("Participants after join:", n_distinct(df_item_task_labeled$participant_id), "\n")
```

```{r exp2_cell_count_table}
df_item_task_labeled %>%
  count(boundary_position, stimulus_type) %>%
  pivot_wider(names_from = stimulus_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 2: RT Analysis Cell Counts") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp2_rt_normality_table}
cells_rt_item <- df_item_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_item, "Exp 2: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp2_rt_qq, fig.height=8}
wrap_plots(
  pmap(list(cells_rt_item$vals, cells_rt_item$label),
       function(v, lbl) qq_plot(v[!is.na(v)], lbl)),
  ncol = 2
)
```

**Normality does not hold -> proceeding with non-parametric tests.**

```{r exp2_rt_test}
rt_test_nonparametric(df_item_task_labeled, "Experiment 2")
```

## 2.4 RT Descriptive Statistics and Plots

```{r exp2_rt_desc}
summary_table(df_item_task_labeled, c("boundary_position", "stimulus_type"),
              "rt", "Exp 2: Encoding RT (ms) - Median and IQR")
```

```{r exp2_rt_violin}
violin_box_plot(df_item_task_labeled,
                x_var = "boundary_position", y_var = "rt",
                facet_var = "stimulus_type",
                title = "Exp 2: Encoding RT by Boundary Condition",
                subtitle = "Diamond = mean",
                x_lab = "Boundary Position", y_lab = "RT (ms)")
```

```{r exp2_rt_bar}
bar_se_plot(df_item_task_labeled,
            x_var = "boundary_position", y_var = "rt",
            facet_var = "stimulus_type",
            title = "Exp 2: Mean Encoding RT",
            subtitle = "Error bars = +/- 1 SE",
            x_lab = "Boundary Position", y_lab = "Mean RT (ms)")
```

## 2.5 REC and LDI

```{r exp2_rec_ldi}
mst_metrics_item <- df_item_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target = mean(stimulus_type == "Target" & response_type == "Old",     na.rm = TRUE),
    p_old_foil   = mean(stimulus_type == "Foil"   & response_type == "Old",     na.rm = TRUE),
    p_sim_lure   = mean(stimulus_type == "Lure"   & response_type == "Similar", na.rm = TRUE),
    p_sim_foil   = mean(stimulus_type == "Foil"   & response_type == "Similar", na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(REC_item = p_old_target - p_old_foil,
         LDI_item = p_sim_lure   - p_sim_foil)

mst_metrics_item %>%
  select(participant_id, REC_item, LDI_item) %>%
  mutate(across(c(REC_item, LDI_item), ~ round(.x, 3))) %>%
  kable(caption = "Exp 2: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

mst_metrics_item %>%
  summarise(
    REC_median = round(median(REC_item), 3), REC_IQR = round(IQR(REC_item), 3),
    LDI_median = round(median(LDI_item), 3), LDI_IQR = round(IQR(LDI_item), 3)
  ) %>%
  kable(caption = "Exp 2: Group REC and LDI Summary (Median / IQR)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

rec_ldi_plot(mst_metrics_item, "REC_item", "LDI_item",
             "Exp 2: Distribution of REC and LDI Scores")
```

## 2.6 Memory Accuracy: Compute, Normality, Descriptives

```{r exp2_accuracy}
boundary_perf_item <- df_item_test %>%
  left_join(
    df_item_task %>% select(participant_id, image_name, boundary_position),
    by = c("participant_id", "image_name")
  ) %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct      = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit        = (stimulus_type == "Target" & response_type == "Old")
  ) %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  ) %>%
  filter(!is.na(boundary_position))

cat("Participants in accuracy data:", n_distinct(boundary_perf_item$participant_id), "\n")
```

```{r exp2_normality_accuracy}
cells_lure_item <- boundary_perf_item %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR", boundary_position, sep = " | "))

cells_target_item <- boundary_perf_item %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit", boundary_position, sep = " | "))

normality_table(cells_lure_item,   "Exp 2: Shapiro-Wilk - Lure CR by Boundary")
normality_table(cells_target_item, "Exp 2: Shapiro-Wilk - Target Hit by Boundary")
```

```{r exp2_accuracy_desc}
summary_table(boundary_perf_item, "boundary_position", "lure_CR",
              "Exp 2: Lure Correct Rejection Rate (Median / IQR)")
summary_table(boundary_perf_item, "boundary_position", "target_hit",
              "Exp 2: Target Hit Rate (Median / IQR)")
```

## 2.7 Memory Accuracy: Plots

```{r exp2_accuracy_violin}
boundary_perf_item %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  violin_box_plot("boundary_position", "acc", facet_var = "measure",
                  title = "Exp 2: Memory Accuracy by Boundary Condition",
                  subtitle = "Diamond = mean",
                  x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

```{r exp2_accuracy_line}
boundary_perf_item %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  boundary_line_plot("boundary_position", "acc", "measure",
                     title = "Exp 2: Memory Accuracy Trend",
                     subtitle = "Error bars = +/- 1/2 IQR",
                     x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

## 2.8 Friedman Test (Non-Parametric Repeated Measures)

```{r exp2_friedman}
friedman_posthoc(boundary_perf_item, "lure_CR",    label = "Exp 2: Lure CR")
friedman_posthoc(boundary_perf_item, "target_hit", label = "Exp 2: Target Hit")
```

## 2.9 One-Sample and Two-Sample Tests

```{r exp2_diff_tests}
perf_diff_item <- boundary_perf_item %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit)) %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

one_sample_test_adaptive(perf_diff_item$lure_pre_diff,    "lure Pre - Non (Exp2)")
one_sample_test_adaptive(perf_diff_item$lure_post_diff,   "lure Post - Non (Exp2)")
one_sample_test_adaptive(perf_diff_item$target_pre_diff,  "target Pre - Non (Exp2)")
one_sample_test_adaptive(perf_diff_item$target_post_diff, "target Post - Non (Exp2)")
```

```{r exp2_diff_plot}
diff_score_plot(perf_diff_item,
                "Exp 2: Difference Scores Relative to Non-Boundary Baseline")
```

## 2.10 Pre vs Post: Paired Wilcoxon Signed-Rank (SAP Section 8)

```{r exp2_paired}
paired_wilcoxon(boundary_perf_item, "lure_CR",    "Exp 2 Lure CR")
paired_wilcoxon(boundary_perf_item, "target_hit", "Exp 2 Target Hit")
```

## 2.11 Linear Mixed-Effects Model (SAP Section 9)

```{r exp2_lme}
run_lme(boundary_perf_item, "lure_CR",    "Exp 2 Lure CR")
run_lme(boundary_perf_item, "target_hit", "Exp 2 Target Hit")
```

## 2.12 Lure Similarity Bin Analysis (SAP Section 10)

```{r exp2_lure_bin}
lure_bin_analysis(df_item_test, df_item_task, "Exp 2")
```

---

# Experiment 3: Task Only

## 3.1 Load and Clean Task Data

```{r exp3_task_load}
task_only_task_files <- list.files(
  "task_only/task_only_data", pattern = "task.*\\.csv$", full.names = TRUE
)
cat("Task-only task files:", length(task_only_task_files), "\n")

load_exp3_task <- function(file_path) {
  df  <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  pid <- substr(basename(file_path), 1, 5)
  if (!"key_resp_9.rt" %in% names(df)) df$key_resp_9.rt <- NA
  if (!"key_resp_8.rt" %in% names(df)) df$key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id    = pid,
      image_name        = basename(image_path),
      trial_number      = trials.thisN + 1,
      rt9               = suppressWarnings(as.numeric(key_resp_9.rt)),
      rt8               = suppressWarnings(as.numeric(key_resp_8.rt)),
      rt = case_when(
        !is.na(rt9) ~ rt9 * 1000,
        !is.na(rt8) ~ (3 + rt8) * 1000,
        TRUE        ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post"))
    )
}

df_task_task <- map_dfr(task_only_task_files, load_exp3_task)
cat("Unique participants:", n_distinct(df_task_task$participant_id), "\n")
```

```{r exp3_task_count_table}
df_task_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 3 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 3.2 Load and Clean Test Data

```{r exp3_test_load}
task_only_test_files <- list.files(
  "task_only/task_only_data", pattern = "test.*\\.csv$", full.names = TRUE
)
cat("Task-only test files:", length(task_only_test_files), "\n")

load_exp3_test <- function(file_path) {
  df <- suppressMessages(read_csv(file_path, show_col_types = FALSE))
  df %>%
    filter(!is.na(trials.thisN)) %>%
    transmute(
      participant_id = as.character(participant),
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_task_test <- map_dfr(task_only_test_files, load_exp3_test)
cat("Unique participants:", n_distinct(df_task_test$participant_id), "\n")
```

```{r exp3_pid_diagnostic}
df_task_task <- df_task_task %>% mutate(participant_id = as.character(as.integer(participant_id)))
df_task_test <- df_task_test %>% mutate(participant_id = as.character(as.integer(participant_id)))
task_pids3 <- sort(unique(df_task_task$participant_id))
test_pids3 <- sort(unique(df_task_test$participant_id))
cat("In task but not test:", setdiff(task_pids3, test_pids3), "\n")
cat("In test but not task:", setdiff(test_pids3, task_pids3), "\n")
```

```{r exp3_test_response_table}
df_task_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 3 Test: Response Counts by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 3.3 Join, Normality Check, and RT Test

```{r exp3_join}
df_task_task_labeled <- df_task_task %>%
  left_join(
    df_task_test %>%
      filter(stimulus_type %in% c("Target", "Lure")) %>%
      select(participant_id, image_name, stimulus_type) %>%
      distinct(),
    by = c("participant_id", "image_name")
  ) %>%
  filter(!is.na(stimulus_type), !is.na(rt)) %>%
  mutate(
    stimulus_type     = factor(stimulus_type),
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    participant_id    = factor(participant_id)
  )

cat("Rows after join:", nrow(df_task_task_labeled), "\n")
cat("Participants after join:", n_distinct(df_task_task_labeled$participant_id), "\n")
```

```{r exp3_cell_count_table}
df_task_task_labeled %>%
  count(boundary_position, stimulus_type) %>%
  pivot_wider(names_from = stimulus_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 3: RT Analysis Cell Counts") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp3_rt_normality_table}
cells_rt_task <- df_task_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_task, "Exp 3: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp3_rt_qq, fig.height=8}
wrap_plots(
  pmap(list(cells_rt_task$vals, cells_rt_task$label),
       function(v, lbl) qq_plot(v[!is.na(v)], lbl)),
  ncol = 2
)
```

**Normality does not hold -> proceeding with non-parametric tests.**

```{r exp3_rt_test}
rt_test_nonparametric(df_task_task_labeled, "Experiment 3")
```

## 3.4 RT Descriptive Statistics and Plots

```{r exp3_rt_desc}
summary_table(df_task_task_labeled, c("boundary_position", "stimulus_type"),
              "rt", "Exp 3: Encoding RT (ms) - Median and IQR")
```

```{r exp3_rt_violin}
violin_box_plot(df_task_task_labeled,
                x_var = "boundary_position", y_var = "rt",
                facet_var = "stimulus_type",
                title = "Exp 3: Encoding RT by Boundary Condition",
                subtitle = "Diamond = mean",
                x_lab = "Boundary Position", y_lab = "RT (ms)")
```

```{r exp3_rt_bar}
bar_se_plot(df_task_task_labeled,
            x_var = "boundary_position", y_var = "rt",
            facet_var = "stimulus_type",
            title = "Exp 3: Mean Encoding RT",
            subtitle = "Error bars = +/- 1 SE",
            x_lab = "Boundary Position", y_lab = "Mean RT (ms)")
```

## 3.5 REC and LDI

```{r exp3_rec_ldi}
mst_metrics_task <- df_task_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target = mean(stimulus_type == "Target" & response_type == "Old",     na.rm = TRUE),
    p_old_foil   = mean(stimulus_type == "Foil"   & response_type == "Old",     na.rm = TRUE),
    p_sim_lure   = mean(stimulus_type == "Lure"   & response_type == "Similar", na.rm = TRUE),
    p_sim_foil   = mean(stimulus_type == "Foil"   & response_type == "Similar", na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(REC_task = p_old_target - p_old_foil,
         LDI_task = p_sim_lure   - p_sim_foil)

mst_metrics_task %>%
  select(participant_id, REC_task, LDI_task) %>%
  mutate(across(c(REC_task, LDI_task), ~ round(.x, 3))) %>%
  kable(caption = "Exp 3: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

mst_metrics_task %>%
  summarise(
    REC_median = round(median(REC_task), 3), REC_IQR = round(IQR(REC_task), 3),
    LDI_median = round(median(LDI_task), 3), LDI_IQR = round(IQR(LDI_task), 3)
  ) %>%
  kable(caption = "Exp 3: Group REC and LDI Summary (Median / IQR)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)

rec_ldi_plot(mst_metrics_task, "REC_task", "LDI_task",
             "Exp 3: Distribution of REC and LDI Scores")
```

## 3.6 Memory Accuracy: Compute, Normality, Descriptives

```{r exp3_accuracy}
boundary_perf_task <- df_task_test %>%
  left_join(
    df_task_task %>% select(participant_id, image_name, boundary_position),
    by = c("participant_id", "image_name")
  ) %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct      = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit        = (stimulus_type == "Target" & response_type == "Old")
  ) %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  ) %>%
  filter(!is.na(boundary_position))

cat("Participants in accuracy data:", n_distinct(boundary_perf_task$participant_id), "\n")
```

```{r exp3_normality_accuracy}
cells_lure_task <- boundary_perf_task %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR", boundary_position, sep = " | "))

cells_target_task <- boundary_perf_task %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit", boundary_position, sep = " | "))

normality_table(cells_lure_task,   "Exp 3: Shapiro-Wilk - Lure CR by Boundary")
normality_table(cells_target_task, "Exp 3: Shapiro-Wilk - Target Hit by Boundary")
```

```{r exp3_accuracy_desc}
summary_table(boundary_perf_task, "boundary_position", "lure_CR",
              "Exp 3: Lure Correct Rejection Rate (Median / IQR)")
summary_table(boundary_perf_task, "boundary_position", "target_hit",
              "Exp 3: Target Hit Rate (Median / IQR)")
```

## 3.7 Memory Accuracy: Plots

```{r exp3_accuracy_violin}
boundary_perf_task %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  violin_box_plot("boundary_position", "acc", facet_var = "measure",
                  title = "Exp 3: Memory Accuracy by Boundary Condition",
                  subtitle = "Diamond = mean",
                  x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

```{r exp3_accuracy_line}
boundary_perf_task %>%
  pivot_longer(c(lure_CR, target_hit), names_to = "measure", values_to = "acc") %>%
  mutate(measure = recode(measure, lure_CR = "Lure CR", target_hit = "Target Hit")) %>%
  boundary_line_plot("boundary_position", "acc", "measure",
                     title = "Exp 3: Memory Accuracy Trend",
                     subtitle = "Error bars = +/- 1/2 IQR",
                     x_lab = "Boundary Position", y_lab = "Proportion Correct")
```

## 3.8 Friedman Test (Non-Parametric Repeated Measures)

```{r exp3_friedman}
friedman_posthoc(boundary_perf_task, "lure_CR",    label = "Exp 3: Lure CR")
friedman_posthoc(boundary_perf_task, "target_hit", label = "Exp 3: Target Hit")
```

## 3.9 One-Sample and Two-Sample Tests

```{r exp3_diff_tests}
perf_diff_task <- boundary_perf_task %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit)) %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

one_sample_test_adaptive(perf_diff_task$lure_pre_diff,    "lure Pre - Non (Exp3)")
one_sample_test_adaptive(perf_diff_task$lure_post_diff,   "lure Post - Non (Exp3)")
one_sample_test_adaptive(perf_diff_task$target_pre_diff,  "target Pre - Non (Exp3)")
one_sample_test_adaptive(perf_diff_task$target_post_diff, "target Post - Non (Exp3)")
```

```{r exp3_diff_plot}
diff_score_plot(perf_diff_task,
                "Exp 3: Difference Scores Relative to Non-Boundary Baseline")
```

## 3.10 Pre vs Post: Paired Wilcoxon Signed-Rank (SAP Section 8)

```{r exp3_paired}
paired_wilcoxon(boundary_perf_task, "lure_CR",    "Exp 3 Lure CR")
paired_wilcoxon(boundary_perf_task, "target_hit", "Exp 3 Target Hit")
```

## 3.11 Linear Mixed-Effects Model (SAP Section 9)

```{r exp3_lme}
run_lme(boundary_perf_task, "lure_CR",    "Exp 3 Lure CR")
run_lme(boundary_perf_task, "target_hit", "Exp 3 Target Hit")
```

## 3.12 Lure Similarity Bin Analysis (SAP Section 10)

```{r exp3_lure_bin}
lure_bin_analysis(df_task_test, df_task_task, "Exp 3")
```
