---
title: "Project Phase 1 Analysis"
author: "Team Popcorn - Amritha, Ahana, Keerthana"
date: "05/3/2026"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
    latex_engine: xelatex
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 3
    theme: flatly
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 8,
  fig.height = 5,
  fig.align  = "center",
  dpi        = 150
)

library(tidyverse)
library(afex)
library(knitr)
library(kableExtra)
library(patchwork)

# Shared plot theme used across all figures
theme_study <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title       = element_text(face = "bold", size = 13, hjust = 0.5,
                                      margin = margin(b = 6)),
      plot.subtitle    = element_text(size = 10, hjust = 0.5, color = "grey40",
                                      margin = margin(b = 10)),
      axis.title       = element_text(size = 11),
      axis.text        = element_text(size = 10),
      strip.text       = element_text(face = "bold", size = 11),
      legend.position  = "none",
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(color = "grey92"),
      plot.margin      = margin(12, 12, 12, 12)
    )
}

# Shared boundary colour palette (Non = blue, Pre = red, Post = green)
bp_colors <- c(Non = "#4D9DE0", Pre = "#E15554", Post = "#3BB273")
```

---

# Helper Functions

```{r helper_functions}
# -------------------------------------------------------
# Normality check via Shapiro-Wilk.
# Prints W, p, and a plain-English decision.
# Returns the shapiro.test object invisibly.
# -------------------------------------------------------
check_normality <- function(x, label = "") {
  x_clean <- x[!is.na(x)]

  if (length(x_clean) < 3) {
    cat(label, "-- too few observations for Shapiro-Wilk\n")
    return(invisible(NULL))
  }
  if (length(x_clean) > 5000) {
    x_clean <- sample(x_clean, 5000)
    cat(label, "-- large sample: Shapiro-Wilk on random 5000 subsample\n")
  }

  sw <- shapiro.test(x_clean)
  cat(sprintf(
    "\nNormality | %s\n  W = %.4f  p = %.4f  --> %s\n",
    label, sw$statistic, sw$p.value,
    ifelse(sw$p.value < 0.05,
           "NON-NORMAL -> use non-parametric",
           "Normal    -> parametric appropriate")
  ))
  return(sw)
}

# -------------------------------------------------------
# One-sample test: t-test if normal, Wilcoxon otherwise.
# -------------------------------------------------------
one_sample_test <- function(x, label = "", mu = 0) {
  sw <- check_normality(x, label)
  cat("  One-sample test vs mu =", mu, "\n")
  if (!is.null(sw) && sw$p.value < 0.05) {
    cat("  => Wilcoxon signed-rank (non-parametric)\n")
    print(wilcox.test(x, mu = mu, exact = FALSE))
  } else {
    cat("  => One-sample t-test (parametric)\n")
    print(t.test(x, mu = mu))
  }
}

# -------------------------------------------------------
# Two-sample test: t-test if both normal, Mann-Whitney otherwise.
# -------------------------------------------------------
two_sample_test <- function(x, y, label_x = "Group1", label_y = "Group2") {
  sw_x <- check_normality(x, label_x)
  sw_y <- check_normality(y, label_y)
  normal_x <- is.null(sw_x) || sw_x$p.value >= 0.05
  normal_y <- is.null(sw_y) || sw_y$p.value >= 0.05
  cat("  Two-sample:", label_x, "vs", label_y, "\n")
  if (normal_x && normal_y) {
    cat("  => Independent-samples t-test (parametric)\n")
    print(t.test(x, y))
  } else {
    cat("  => Mann-Whitney U (non-parametric)\n")
    print(wilcox.test(x, y, exact = FALSE))
  }
}

# -------------------------------------------------------
# Shapiro-Wilk results as a formatted kable table.
# cells_df must have columns: label, vals (list-column).
# -------------------------------------------------------
normality_table <- function(cells_df,
                            caption_text = "Shapiro-Wilk Normality Results") {
  results <- map_dfr(seq_len(nrow(cells_df)), function(i) {
    v <- cells_df$vals[[i]]
    v <- v[!is.na(v)]
    if (length(v) < 3) {
      return(tibble(Condition = cells_df$label[i],
                    n = length(v), W = NA, p = NA, Normal = "Too few obs"))
    }
    sw <- shapiro.test(v)
    tibble(
      Condition = cells_df$label[i],
      n         = length(v),
      W         = round(sw$statistic, 4),
      p         = round(sw$p.value,   4),
      Normal    = ifelse(sw$p.value >= 0.05, "Yes", "No")
    )
  })

  results %>%
    kable(caption = caption_text, align = "lrrrr") %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE, font_size = 12
    ) %>%
    column_spec(5, bold = TRUE,
                color = ifelse(results$Normal == "Yes", "#3BB273", "#E15554"))
}

# -------------------------------------------------------
# Descriptive statistics table: mean, SD, SE, 95% CI.
# -------------------------------------------------------
summary_table <- function(df, group_vars, dv,
                          caption_text = "Descriptive Statistics") {
  df %>%
    group_by(across(all_of(group_vars))) %>%
    summarise(
      n          = sum(!is.na(.data[[dv]])),
      Mean       = round(mean(.data[[dv]], na.rm = TRUE), 3),
      SD         = round(sd(.data[[dv]],   na.rm = TRUE), 3),
      SE         = round(SD / sqrt(n), 3),
      CI95_lower = round(Mean - 1.96 * SE, 3),
      CI95_upper = round(Mean + 1.96 * SE, 3),
      .groups    = "drop"
    ) %>%
    kable(caption = caption_text, align = "llrrrrrr") %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE, font_size = 12
    )
}

# -------------------------------------------------------
# Violin + boxplot + mean diamond.
# -------------------------------------------------------
violin_box_plot <- function(df, x_var, y_var, fill_var = x_var,
                            title = "", subtitle = "",
                            x_lab = x_var, y_lab = y_var,
                            facet_var = NULL,
                            colors = bp_colors) {
  p <- ggplot(df, aes(x = .data[[x_var]],
                      y = .data[[y_var]],
                      fill = .data[[fill_var]])) +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30",
                 outlier.size = 1.5, outlier.alpha = 0.5) +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(values = colors) +
    labs(title = title, subtitle = subtitle, x = x_lab, y = y_lab) +
    theme_study()

  if (!is.null(facet_var))
    p <- p + facet_wrap(as.formula(paste("~", facet_var)))

  return(p)
}

# -------------------------------------------------------
# Bar chart with +/- 1 SE error bars.
# -------------------------------------------------------
bar_se_plot <- function(df, x_var, y_var,
                        title = "", subtitle = "",
                        x_lab = x_var, y_lab = y_var,
                        facet_var = NULL,
                        colors = bp_colors) {
  sum_df <- df %>%
    group_by(across(all_of(c(x_var, facet_var)))) %>%
    summarise(
      mean_val = mean(.data[[y_var]], na.rm = TRUE),
      se_val   = sd(.data[[y_var]],  na.rm = TRUE) / sqrt(n()),
      .groups  = "drop"
    )

  p <- ggplot(sum_df, aes(x = .data[[x_var]],
                           y = mean_val,
                           fill = .data[[x_var]])) +
    geom_col(width = 0.6, alpha = 0.85, color = "white") +
    geom_errorbar(aes(ymin = mean_val - se_val,
                      ymax = mean_val + se_val),
                  width = 0.2, color = "grey30", linewidth = 0.7) +
    scale_fill_manual(values = colors) +
    labs(title = title, subtitle = subtitle, x = x_lab, y = y_lab) +
    theme_study()

  if (!is.null(facet_var))
    p <- p + facet_wrap(as.formula(paste("~", facet_var)))

  return(p)
}

# -------------------------------------------------------
# Line plot of means across boundary positions.
# -------------------------------------------------------
boundary_line_plot <- function(df, x_var, y_var, group_var,
                               title = "", subtitle = "",
                               x_lab = x_var, y_lab = y_var,
                               colors = c("#E15554", "#3BB273")) {
  sum_df <- df %>%
    group_by(across(all_of(c(x_var, group_var)))) %>%
    summarise(
      mean_val = mean(.data[[y_var]], na.rm = TRUE),
      se_val   = sd(.data[[y_var]],  na.rm = TRUE) / sqrt(n()),
      .groups  = "drop"
    )

  ggplot(sum_df, aes(x = .data[[x_var]],
                     y = mean_val,
                     color = .data[[group_var]],
                     group = .data[[group_var]])) +
    geom_line(linewidth = 1.1) +
    geom_point(size = 3.5) +
    geom_errorbar(aes(ymin = mean_val - se_val,
                      ymax = mean_val + se_val),
                  width = 0.15, linewidth = 0.7) +
    scale_color_manual(values = colors) +
    labs(title = title, subtitle = subtitle,
         x = x_lab, y = y_lab, color = group_var) +
    theme_study() +
    theme(legend.position = "right")
}

# -------------------------------------------------------
# Q-Q plot for visual normality inspection.
# -------------------------------------------------------
qq_plot <- function(x, label = "") {
  tibble(vals = x) %>%
    ggplot(aes(sample = vals)) +
    stat_qq(color = "#4D9DE0", alpha = 0.7, size = 1.5) +
    stat_qq_line(color = "#E15554", linewidth = 0.9) +
    labs(title    = paste("Q-Q Plot:", label),
         subtitle = "Points close to line indicate normality",
         x = "Theoretical Quantiles",
         y = "Sample Quantiles") +
    theme_study()
}

# -------------------------------------------------------
# Difference score violin plot (Pre-Non and Post-Non).
# -------------------------------------------------------
diff_score_plot <- function(diff_df, title = "") {
  diff_df %>%
    select(participant_id, lure_pre_diff, lure_post_diff,
           target_pre_diff, target_post_diff) %>%
    pivot_longer(-participant_id, names_to = "contrast", values_to = "diff") %>%
    mutate(
      Measure   = ifelse(str_detect(contrast, "lure"), "Lure CR", "Target Hit"),
      Condition = ifelse(str_detect(contrast, "pre"),  "Pre - Non", "Post - Non")
    ) %>%
    ggplot(aes(x = Condition, y = diff, fill = Condition)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30") +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(
      values = c("Pre - Non" = "#E15554", "Post - Non" = "#3BB273")
    ) +
    facet_wrap(~ Measure) +
    labs(
      title    = title,
      subtitle = "Dashed line = 0 (no difference from baseline)",
      x        = "Contrast",
      y        = "Difference in Proportion Correct"
    ) +
    theme_study()
}

# -------------------------------------------------------
# REC / LDI violin plot.
# -------------------------------------------------------
rec_ldi_plot <- function(metrics_df, rec_col, ldi_col, title = "") {
  metrics_df %>%
    pivot_longer(cols = c(all_of(rec_col), all_of(ldi_col)),
                 names_to = "Metric", values_to = "Value") %>%
    mutate(Metric = recode(Metric,
                           !!rec_col := "REC", !!ldi_col := "LDI")) %>%
    ggplot(aes(x = Metric, y = Value, fill = Metric)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_violin(alpha = 0.55, trim = FALSE, color = NA) +
    geom_boxplot(width = 0.18, fill = "white", color = "grey30",
                 outlier.size = 1.5, outlier.alpha = 0.5) +
    stat_summary(fun = mean, geom = "point",
                 shape = 23, size = 3, fill = "white", color = "grey20") +
    scale_fill_manual(values = c(REC = "#4D9DE0", LDI = "#E15554")) +
    labs(title    = title,
         subtitle = "Dashed line = chance (0)",
         x = "Metric", y = "Score") +
    theme_study()
}
```

---

# Experiment 1: Both Item and Task

## 1.1 Load and Clean Task Data

```{r exp1_task_load}
base_path <- "Both_item_task"
task_path <- file.path(base_path, "both_data")

task_files <- list.files(
  path = task_path, pattern = "_MST_task_.*\\.csv$", full.names = TRUE
)
cat("Task files found:", length(task_files), "\n")

load_task_clean <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  participant_id <- substr(basename(file_path), 1, 5)
  if (!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if (!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN,
           trials.key_resp_9.rt, trials.key_resp_8.rt) %>%
    mutate(
      participant_id       = participant_id,
      trial_number         = trials.thisN + 1,
      trials.key_resp_9.rt = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      trials.key_resp_8.rt = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      rt = case_when(
        !is.na(trials.key_resp_9.rt) ~ trials.key_resp_9.rt * 1000,
        !is.na(trials.key_resp_8.rt) ~ (3 + trials.key_resp_8.rt) * 1000,
        TRUE                         ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post")),
      image_name = basename(image_path)
    )
}

df_both_task <- map_dfr(task_files, load_task_clean)
cat("Unique participants:", length(unique(df_both_task$participant_id)), "\n")
```

```{r exp1_task_count_table}
df_both_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 1 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.2 Load and Clean Test Data

```{r exp1_test_load}
test_files <- list.files(
  path = task_path, pattern = "_MST_test_.*\\.csv$", full.names = TRUE
)
cat("Test files found:", length(test_files), "\n")

load_test_clean <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN, trials.key_resp_3.keys,
           trials.key_resp_3.rt, position_of_stimuli, participant) %>%
    mutate(
      participant_id = participant,
      trial_number   = trials.thisN + 1,
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_both_test <- map_dfr(test_files, load_test_clean)
cat("Unique participants:", length(unique(df_both_test$participant_id)), "\n")
```

```{r exp1_test_response_table}
df_both_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 1 Test: Response Count by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.3 Join Stimulus Type to Encoding Data

```{r exp1_join_stimulus}
stimulus_lookup_both <- df_both_test %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  select(participant_id, image_name, stimulus_type) %>%
  distinct()

df_both_task_labeled <- df_both_task %>%
  left_join(stimulus_lookup_both, by = c("participant_id", "image_name")) %>%
  filter(!is.na(stimulus_type)) %>%
  mutate(stimulus_type = factor(stimulus_type))

cat("Rows with stimulus label:", nrow(df_both_task_labeled), "\n")
```

```{r exp1_cell_count_table}
df_both_task_labeled %>%
  count(boundary_position, stimulus_type, name = "n") %>%
  pivot_wider(names_from = stimulus_type, values_from = n) %>%
  kable(caption = "Exp 1: Cell Counts (Boundary x Stimulus Type) for RT Analysis") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 1.4 Normality Check: Encoding RT

```{r exp1_rt_normality}
cells_rt_both <- df_both_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_both,
                "Exp 1: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp1_rt_qq, fig.height=8}
qq_plots_both <- pmap(
  list(cells_rt_both$vals, cells_rt_both$label),
  function(v, lbl) qq_plot(v[!is.na(v)], lbl)
)
wrap_plots(qq_plots_both, ncol = 2)
```

## 1.5 Encoding RT: Descriptive Statistics

```{r exp1_rt_desc_table}
summary_table(
  df_both_task_labeled,
  group_vars   = c("boundary_position", "stimulus_type"),
  dv           = "rt",
  caption_text = "Exp 1: Encoding RT (ms) - Mean, SD, SE, 95% CI"
)
```

## 1.6 Encoding RT: Plots

```{r exp1_rt_violin}
violin_box_plot(
  df        = df_both_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 1: Encoding RT by Boundary Condition",
  subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
  x_lab     = "Boundary Position",
  y_lab     = "Reaction Time (ms)"
)
```

```{r exp1_rt_bar}
bar_se_plot(
  df        = df_both_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 1: Mean Encoding RT by Boundary Condition",
  subtitle  = "Error bars = +/- 1 SE",
  x_lab     = "Boundary Position",
  y_lab     = "Mean RT (ms)"
)
```

## 1.7 Two-Way ANOVA or ART: RT ~ Boundary x Stimulus Type

```{r exp1_rt_anova}
all_normal_both_rt <- all(map_lgl(cells_rt_both$vals, function(v) {
  v <- v[!is.na(v)]
  if (length(v) < 3) return(TRUE)
  shapiro.test(v)$p.value >= 0.05
}))

if (all_normal_both_rt) {
  cat("All cells normal -> Two-way ANOVA\n\n")
  rt_anova_both <- aov(rt ~ boundary_position * stimulus_type,
                       data = df_both_task_labeled)
  print(summary(rt_anova_both))
  cat("\nTukey HSD post-hoc (boundary_position):\n")
  print(TukeyHSD(rt_anova_both, which = "boundary_position"))
} else {
  cat("Non-normality detected -> Aligned Ranks Transformation ANOVA\n\n")
  if (!requireNamespace("ARTool", quietly = TRUE))
    install.packages("ARTool", repos = "https://cloud.r-project.org")
  library(ARTool)
  art_model_both <- art(
    rt ~ boundary_position * stimulus_type + Error(participant_id),
    data = df_both_task_labeled
  )
  print(anova(art_model_both))
  cat("\nART pairwise contrasts (boundary_position):\n")
  print(summary(art.con(art_model_both, "boundary_position",
                        adjust = "bonferroni")))
}
```

## 1.8 REC and LDI Metrics

```{r exp1_rec_ldi}
participant_probs_both <- df_both_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target   = mean(stimulus_type == "Target" & response_type == "Old"),
    p_old_foil     = mean(stimulus_type == "Foil"   & response_type == "Old"),
    p_similar_lure = mean(stimulus_type == "Lure"   & response_type == "Similar"),
    p_similar_foil = mean(stimulus_type == "Foil"   & response_type == "Similar"),
    .groups = "drop"
  )

mst_metrics_both <- participant_probs_both %>%
  mutate(REC = p_old_target - p_old_foil,
         LDI = p_similar_lure - p_similar_foil)
```

```{r exp1_rec_ldi_participant_table}
mst_metrics_both %>%
  select(participant_id, REC, LDI) %>%
  mutate(across(c(REC, LDI), ~ round(.x, 3))) %>%
  kable(caption = "Exp 1: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp1_rec_ldi_summary_table}
mst_metrics_both %>%
  summarise(
    REC_mean = round(mean(REC), 3), REC_sd = round(sd(REC), 3),
    LDI_mean = round(mean(LDI), 3), LDI_sd = round(sd(LDI), 3)
  ) %>%
  kable(caption = "Exp 1: Group-Level REC and LDI Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp1_rec_ldi_plot}
rec_ldi_plot(mst_metrics_both, "REC", "LDI",
             "Exp 1: Distribution of REC and LDI Scores")
```

## 1.9 Memory Accuracy: Join and Compute

```{r exp1_accuracy_join}
encoding_lookup_both <- df_both_task %>%
  select(participant_id, image_name, boundary_position)

df_both_joined <- df_both_test %>%
  left_join(encoding_lookup_both, by = c("participant_id", "image_name")) %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit   = (stimulus_type == "Target" & response_type == "Old")
  )

boundary_perf_both <- df_both_joined %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  )
```

## 1.10 Normality Check: Memory Accuracy

```{r exp1_accuracy_normality}
cells_lure_both <- boundary_perf_both %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR |", boundary_position))

cells_target_both <- boundary_perf_both %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit |", boundary_position))

normality_table(cells_lure_both,
                "Exp 1: Shapiro-Wilk - Lure Correct Rejection by Boundary")
normality_table(cells_target_both,
                "Exp 1: Shapiro-Wilk - Target Hit Rate by Boundary")
```

## 1.11 Memory Accuracy: Descriptive Statistics

```{r exp1_accuracy_desc_tables}
summary_table(boundary_perf_both,
              group_vars   = "boundary_position",
              dv           = "lure_CR",
              caption_text = "Exp 1: Lure Correct Rejection Rate by Boundary Position")

summary_table(boundary_perf_both,
              group_vars   = "boundary_position",
              dv           = "target_hit",
              caption_text = "Exp 1: Target Hit Rate by Boundary Position")
```

## 1.12 Memory Accuracy: Plots

```{r exp1_accuracy_violin}
boundary_perf_both %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  violin_box_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    facet_var = "measure",
    title     = "Exp 1: Memory Accuracy by Boundary Condition",
    subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

```{r exp1_accuracy_line}
boundary_perf_both %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  boundary_line_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    group_var = "measure",
    title     = "Exp 1: Memory Accuracy Trend Across Boundary Positions",
    subtitle  = "Error bars = +/- 1 SE",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

## 1.13 Repeated Measures ANOVA

```{r exp1_rm_anova}
cat("--- RM-ANOVA: lure_CR ~ boundary_position ---\n")
rm_lure_both <- aov_ez(id = "participant_id", dv = "lure_CR",
                       data = boundary_perf_both, within = "boundary_position")
print(rm_lure_both)

cat("\n--- RM-ANOVA: target_hit ~ boundary_position ---\n")
rm_target_both <- aov_ez(id = "participant_id", dv = "target_hit",
                         data = boundary_perf_both, within = "boundary_position")
print(rm_target_both)
```

## 1.14 One-Sample Tests: Boundary vs Baseline

```{r exp1_one_sample}
perf_wide_both <- boundary_perf_both %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit))

perf_diff_both <- perf_wide_both %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

cat("=== lure_CR: Pre - Non ===\n")
one_sample_test(perf_diff_both$lure_pre_diff,    "lure Pre-Non (Exp1)")
cat("\n=== lure_CR: Post - Non ===\n")
one_sample_test(perf_diff_both$lure_post_diff,   "lure Post-Non (Exp1)")
cat("\n=== target_hit: Pre - Non ===\n")
one_sample_test(perf_diff_both$target_pre_diff,  "target Pre-Non (Exp1)")
cat("\n=== target_hit: Post - Non ===\n")
one_sample_test(perf_diff_both$target_post_diff, "target Post-Non (Exp1)")
```

```{r exp1_diff_plot}
diff_score_plot(perf_diff_both,
                "Exp 1: Difference Scores Relative to Non-Boundary Baseline")
```

## 1.15 Two-Sample Tests: Pre vs Post

```{r exp1_two_sample}
cat("=== lure_CR: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_both$lure_CR[boundary_perf_both$boundary_position == "Pre"],
  boundary_perf_both$lure_CR[boundary_perf_both$boundary_position == "Post"],
  "lure Pre (Exp1)", "lure Post (Exp1)"
)
cat("\n=== target_hit: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_both$target_hit[boundary_perf_both$boundary_position == "Pre"],
  boundary_perf_both$target_hit[boundary_perf_both$boundary_position == "Post"],
  "target Pre (Exp1)", "target Post (Exp1)"
)
```

---

# Experiment 2: Item Only

## 2.1 Load and Clean Task Data

```{r exp2_task_load}
item_base_path <- "item_only"
item_task_path <- file.path(item_base_path, "item_only_data")

item_task_files <- list.files(
  path = item_task_path, pattern = "_MST_task_.*\\.csv$", full.names = TRUE
)
cat("Item task files:", length(item_task_files), "\n")

load_item_task <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  participant_id <- substr(basename(file_path), 1, 5)
  if (!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if (!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN,
           trials.key_resp_9.rt, trials.key_resp_8.rt) %>%
    mutate(
      participant_id       = participant_id,
      trial_number         = trials.thisN + 1,
      trials.key_resp_9.rt = as.numeric(trials.key_resp_9.rt),
      trials.key_resp_8.rt = as.numeric(trials.key_resp_8.rt),
      rt = case_when(
        !is.na(trials.key_resp_9.rt) ~ trials.key_resp_9.rt * 1000,
        !is.na(trials.key_resp_8.rt) ~ (3 + trials.key_resp_8.rt) * 1000,
        TRUE                         ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post")),
      image_name = basename(image_path)
    )
}

df_item_task <- map_dfr(item_task_files, load_item_task)
cat("Unique participants:", length(unique(df_item_task$participant_id)), "\n")
```

```{r exp2_task_count_table}
df_item_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 2 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 2.2 Load and Clean Test Data

```{r exp2_test_load}
item_test_files <- list.files(
  path = item_task_path, pattern = "_MST_test_.*\\.csv$", full.names = TRUE
)
cat("Item test files:", length(item_test_files), "\n")

load_item_test <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN, trials.key_resp_3.keys,
           trials.key_resp_3.rt, position_of_stimuli, participant) %>%
    mutate(
      participant_id = participant,
      trial_number   = trials.thisN + 1,
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_item_test <- map_dfr(item_test_files, load_item_test)
cat("Unique participants:", length(unique(df_item_test$participant_id)), "\n")
```

```{r exp2_test_response_table}
df_item_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 2 Test: Response Count by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 2.3 Join Stimulus Type to Encoding Data

```{r exp2_join_stimulus}
stimulus_lookup_item <- df_item_test %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  select(participant_id, image_name, stimulus_type) %>%
  distinct()

df_item_task_labeled <- df_item_task %>%
  left_join(stimulus_lookup_item, by = c("participant_id", "image_name")) %>%
  filter(!is.na(stimulus_type)) %>%
  mutate(stimulus_type = factor(stimulus_type))

cat("Rows with label:", nrow(df_item_task_labeled), "\n")
```

```{r exp2_cell_count_table}
df_item_task_labeled %>%
  count(boundary_position, stimulus_type, name = "n") %>%
  pivot_wider(names_from = stimulus_type, values_from = n) %>%
  kable(caption = "Exp 2: Cell Counts (Boundary x Stimulus Type) for RT Analysis") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 2.4 Normality Check: Encoding RT

```{r exp2_rt_normality}
cells_rt_item <- df_item_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_item,
                "Exp 2: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp2_rt_qq, fig.height=8}
qq_plots_item <- pmap(
  list(cells_rt_item$vals, cells_rt_item$label),
  function(v, lbl) qq_plot(v[!is.na(v)], lbl)
)
wrap_plots(qq_plots_item, ncol = 2)
```

## 2.5 Encoding RT: Descriptive Statistics

```{r exp2_rt_desc_table}
summary_table(
  df_item_task_labeled,
  group_vars   = c("boundary_position", "stimulus_type"),
  dv           = "rt",
  caption_text = "Exp 2: Encoding RT (ms) - Mean, SD, SE, 95% CI"
)
```

## 2.6 Encoding RT: Plots

```{r exp2_rt_violin}
violin_box_plot(
  df        = df_item_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 2: Encoding RT by Boundary Condition",
  subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
  x_lab     = "Boundary Position",
  y_lab     = "Reaction Time (ms)"
)
```

```{r exp2_rt_bar}
bar_se_plot(
  df        = df_item_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 2: Mean Encoding RT by Boundary Condition",
  subtitle  = "Error bars = +/- 1 SE",
  x_lab     = "Boundary Position",
  y_lab     = "Mean RT (ms)"
)
```

## 2.7 Two-Way ANOVA or ART: RT ~ Boundary x Stimulus Type

```{r exp2_rt_anova}
all_normal_item_rt <- all(map_lgl(cells_rt_item$vals, function(v) {
  v <- v[!is.na(v)]
  if (length(v) < 3) return(TRUE)
  shapiro.test(v)$p.value >= 0.05
}))

if (all_normal_item_rt) {
  cat("All cells normal -> Two-way ANOVA\n\n")
  rt_anova_item <- aov(rt ~ boundary_position * stimulus_type,
                       data = df_item_task_labeled)
  print(summary(rt_anova_item))
  cat("\nTukey HSD post-hoc (boundary_position):\n")
  print(TukeyHSD(rt_anova_item, which = "boundary_position"))
} else {
  cat("Non-normality detected -> ART ANOVA\n\n")
  if (!requireNamespace("ARTool", quietly = TRUE))
    install.packages("ARTool", repos = "https://cloud.r-project.org")
  library(ARTool)
  art_model_item <- art(
    rt ~ boundary_position * stimulus_type + Error(participant_id),
    data = df_item_task_labeled
  )
  print(anova(art_model_item))
  cat("\nART pairwise contrasts:\n")
  print(summary(art.con(art_model_item, "boundary_position",
                        adjust = "bonferroni")))
}
```

## 2.8 REC and LDI Metrics

```{r exp2_rec_ldi}
participant_probs_item <- df_item_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target   = mean(stimulus_type == "Target" & response_type == "Old"),
    p_old_foil     = mean(stimulus_type == "Foil"   & response_type == "Old"),
    p_similar_lure = mean(stimulus_type == "Lure"   & response_type == "Similar"),
    p_similar_foil = mean(stimulus_type == "Foil"   & response_type == "Similar"),
    .groups = "drop"
  )

mst_metrics_item <- participant_probs_item %>%
  mutate(REC_item = p_old_target - p_old_foil,
         LDI_item = p_similar_lure - p_similar_foil)
```

```{r exp2_rec_ldi_participant_table}
mst_metrics_item %>%
  select(participant_id, REC_item, LDI_item) %>%
  mutate(across(c(REC_item, LDI_item), ~ round(.x, 3))) %>%
  kable(caption = "Exp 2: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp2_rec_ldi_summary_table}
mst_metrics_item %>%
  summarise(
    REC_mean = round(mean(REC_item), 3), REC_sd = round(sd(REC_item), 3),
    LDI_mean = round(mean(LDI_item), 3), LDI_sd = round(sd(LDI_item), 3)
  ) %>%
  kable(caption = "Exp 2: Group-Level REC and LDI Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp2_rec_ldi_plot}
rec_ldi_plot(mst_metrics_item, "REC_item", "LDI_item",
             "Exp 2: Distribution of REC and LDI Scores")
```

## 2.9 Memory Accuracy: Join and Compute

```{r exp2_accuracy_join}
encoding_lookup_item <- df_item_task %>%
  select(participant_id, image_name, boundary_position)

df_item_joined <- df_item_test %>%
  left_join(encoding_lookup_item,
            by = c("participant_id", "image_name"),
            relationship = "many-to-many") %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit   = (stimulus_type == "Target" & response_type == "Old")
  )

boundary_perf_item <- df_item_joined %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  )
```

## 2.10 Normality Check: Memory Accuracy

```{r exp2_accuracy_normality}
cells_lure_item <- boundary_perf_item %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR |", boundary_position))

cells_target_item <- boundary_perf_item %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit |", boundary_position))

normality_table(cells_lure_item,
                "Exp 2: Shapiro-Wilk - Lure Correct Rejection by Boundary")
normality_table(cells_target_item,
                "Exp 2: Shapiro-Wilk - Target Hit Rate by Boundary")
```

## 2.11 Memory Accuracy: Descriptive Statistics

```{r exp2_accuracy_desc_tables}
summary_table(boundary_perf_item,
              group_vars   = "boundary_position",
              dv           = "lure_CR",
              caption_text = "Exp 2: Lure Correct Rejection Rate by Boundary Position")

summary_table(boundary_perf_item,
              group_vars   = "boundary_position",
              dv           = "target_hit",
              caption_text = "Exp 2: Target Hit Rate by Boundary Position")
```

## 2.12 Memory Accuracy: Plots

```{r exp2_accuracy_violin}
boundary_perf_item %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  violin_box_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    facet_var = "measure",
    title     = "Exp 2: Memory Accuracy by Boundary Condition",
    subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

```{r exp2_accuracy_line}
boundary_perf_item %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  boundary_line_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    group_var = "measure",
    title     = "Exp 2: Memory Accuracy Trend Across Boundary Positions",
    subtitle  = "Error bars = +/- 1 SE",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

## 2.13 Repeated Measures ANOVA

```{r exp2_rm_anova}
cat("--- RM-ANOVA: lure_CR ~ boundary_position ---\n")
rm_lure_item <- aov_ez(id = "participant_id", dv = "lure_CR",
                       data = boundary_perf_item, within = "boundary_position")
print(rm_lure_item)

cat("\n--- RM-ANOVA: target_hit ~ boundary_position ---\n")
rm_target_item <- aov_ez(id = "participant_id", dv = "target_hit",
                         data = boundary_perf_item, within = "boundary_position")
print(rm_target_item)
```

## 2.14 One-Sample Tests: Boundary vs Baseline

```{r exp2_one_sample}
perf_wide_item <- boundary_perf_item %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit))

perf_diff_item <- perf_wide_item %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

cat("=== lure_CR: Pre - Non ===\n")
one_sample_test(perf_diff_item$lure_pre_diff,    "lure Pre-Non (Exp2)")
cat("\n=== lure_CR: Post - Non ===\n")
one_sample_test(perf_diff_item$lure_post_diff,   "lure Post-Non (Exp2)")
cat("\n=== target_hit: Pre - Non ===\n")
one_sample_test(perf_diff_item$target_pre_diff,  "target Pre-Non (Exp2)")
cat("\n=== target_hit: Post - Non ===\n")
one_sample_test(perf_diff_item$target_post_diff, "target Post-Non (Exp2)")
```

```{r exp2_diff_plot}
diff_score_plot(perf_diff_item,
                "Exp 2: Difference Scores Relative to Non-Boundary Baseline")
```

## 2.15 Two-Sample Tests: Pre vs Post

```{r exp2_two_sample}
cat("=== lure_CR: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_item$lure_CR[boundary_perf_item$boundary_position == "Pre"],
  boundary_perf_item$lure_CR[boundary_perf_item$boundary_position == "Post"],
  "lure Pre (Exp2)", "lure Post (Exp2)"
)
cat("\n=== target_hit: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_item$target_hit[boundary_perf_item$boundary_position == "Pre"],
  boundary_perf_item$target_hit[boundary_perf_item$boundary_position == "Post"],
  "target Pre (Exp2)", "target Post (Exp2)"
)
```

---

# Experiment 3: Task Only

## 3.1 Load and Clean Task Data

```{r exp3_task_load}
task_only_base <- "task_only"
task_only_path <- file.path(task_only_base, "task_only_data")

task_only_task_files <- list.files(
  path = task_only_path, pattern = "task.*\\.csv$", full.names = TRUE
)
cat("Task-only task files:", length(task_only_task_files), "\n")

load_task_only_task <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  participant_id <- substr(basename(file_path), 1, 5)
  if (!"trials.key_resp_9.rt" %in% names(df)) df$trials.key_resp_9.rt <- NA
  if (!"trials.key_resp_8.rt" %in% names(df)) df$trials.key_resp_8.rt <- NA
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN,
           trials.key_resp_9.rt, trials.key_resp_8.rt) %>%
    mutate(
      participant_id       = participant_id,
      trial_number         = trials.thisN + 1,
      trials.key_resp_9.rt = suppressWarnings(as.numeric(trials.key_resp_9.rt)),
      trials.key_resp_8.rt = suppressWarnings(as.numeric(trials.key_resp_8.rt)),
      rt = case_when(
        !is.na(trials.key_resp_9.rt) ~ trials.key_resp_9.rt * 1000,
        !is.na(trials.key_resp_8.rt) ~ (3 + trials.key_resp_8.rt) * 1000,
        TRUE                         ~ NA_real_
      ),
      event_position    = ((trial_number - 1) %% 7) + 1,
      boundary_position = factor(case_when(
        event_position == 1 ~ "Post",
        event_position == 7 ~ "Pre",
        TRUE                ~ "Non"
      ), levels = c("Non", "Pre", "Post")),
      image_name = basename(image_path)
    )
}

df_task_task <- map_dfr(task_only_task_files, load_task_only_task)
cat("Unique participants:", length(unique(df_task_task$participant_id)), "\n")
```

```{r exp3_task_count_table}
df_task_task %>%
  count(boundary_position, name = "Trial Count") %>%
  kable(caption = "Exp 3 Task: Trial Counts by Boundary Position") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 3.2 Load and Clean Test Data

```{r exp3_test_load}
task_only_test_files <- list.files(
  path = task_only_path, pattern = "test.*\\.csv$", full.names = TRUE
)
cat("Task-only test files:", length(task_only_test_files), "\n")

load_task_only_test <- function(file_path) {
  df <- suppressMessages(
    read_csv(file_path, show_col_types = FALSE, name_repair = "unique")
  )
  df %>%
    filter(!is.na(trials.thisN)) %>%
    select(image_path, trials.thisN, trials.key_resp_3.keys,
           trials.key_resp_3.rt, position_of_stimuli, participant) %>%
    mutate(
      participant_id = participant,
      trial_number   = trials.thisN + 1,
      image_name     = basename(image_path),
      stimulus_type  = case_when(
        str_detect(image_name, "^Foils")   ~ "Foil",
        str_detect(image_name, "b\\.jpg$") ~ "Lure",
        str_detect(image_name, "a\\.jpg$") ~ "Target",
        TRUE                               ~ NA_character_
      ),
      response_type = case_when(
        trials.key_resp_3.keys == "o" ~ "Old",
        trials.key_resp_3.keys == "s" ~ "Similar",
        trials.key_resp_3.keys == "n" ~ "New",
        TRUE                          ~ NA_character_
      )
    )
}

df_task_test <- map_dfr(task_only_test_files, load_task_only_test)
cat("Unique participants:", length(unique(df_task_test$participant_id)), "\n")
```

```{r exp3_test_response_table}
df_task_test %>%
  filter(!is.na(stimulus_type), !is.na(response_type)) %>%
  count(stimulus_type, response_type) %>%
  pivot_wider(names_from = response_type, values_from = n, values_fill = 0) %>%
  kable(caption = "Exp 3 Test: Response Count by Stimulus Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 3.3 Join Stimulus Type to Encoding Data

```{r exp3_join_stimulus}
stimulus_lookup_task <- df_task_test %>%
  filter(stimulus_type %in% c("Target", "Lure")) %>%
  select(participant_id, image_name, stimulus_type) %>%
  distinct()

df_task_task_labeled <- df_task_task %>%
  left_join(stimulus_lookup_task, by = c("participant_id", "image_name")) %>%
  filter(!is.na(stimulus_type)) %>%
  mutate(stimulus_type = factor(stimulus_type))

cat("Rows with label:", nrow(df_task_task_labeled), "\n")
```

```{r exp3_cell_count_table}
df_task_task_labeled %>%
  count(boundary_position, stimulus_type, name = "n") %>%
  pivot_wider(names_from = stimulus_type, values_from = n) %>%
  kable(caption = "Exp 3: Cell Counts (Boundary x Stimulus Type) for RT Analysis") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

## 3.4 Normality Check: Encoding RT

```{r exp3_rt_normality}
cells_rt_task <- df_task_task_labeled %>%
  group_by(boundary_position, stimulus_type) %>%
  summarise(vals = list(rt), .groups = "drop") %>%
  mutate(label = paste(boundary_position, stimulus_type, sep = " | "))

normality_table(cells_rt_task,
                "Exp 3: Shapiro-Wilk - Encoding RT by Cell")
```

```{r exp3_rt_qq, fig.height=8}
qq_plots_task <- pmap(
  list(cells_rt_task$vals, cells_rt_task$label),
  function(v, lbl) qq_plot(v[!is.na(v)], lbl)
)
wrap_plots(qq_plots_task, ncol = 2)
```

## 3.5 Encoding RT: Descriptive Statistics

```{r exp3_rt_desc_table}
summary_table(
  df_task_task_labeled,
  group_vars   = c("boundary_position", "stimulus_type"),
  dv           = "rt",
  caption_text = "Exp 3: Encoding RT (ms) - Mean, SD, SE, 95% CI"
)
```

## 3.6 Encoding RT: Plots

```{r exp3_rt_violin}
violin_box_plot(
  df        = df_task_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 3: Encoding RT by Boundary Condition",
  subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
  x_lab     = "Boundary Position",
  y_lab     = "Reaction Time (ms)"
)
```

```{r exp3_rt_bar}
bar_se_plot(
  df        = df_task_task_labeled,
  x_var     = "boundary_position",
  y_var     = "rt",
  facet_var = "stimulus_type",
  title     = "Exp 3: Mean Encoding RT by Boundary Condition",
  subtitle  = "Error bars = +/- 1 SE",
  x_lab     = "Boundary Position",
  y_lab     = "Mean RT (ms)"
)
```

## 3.7 Two-Way ANOVA or ART: RT ~ Boundary x Stimulus Type

```{r exp3_rt_anova}
all_normal_task_rt <- all(map_lgl(cells_rt_task$vals, function(v) {
  v <- v[!is.na(v)]
  if (length(v) < 3) return(TRUE)
  shapiro.test(v)$p.value >= 0.05
}))

if (all_normal_task_rt) {
  cat("All cells normal -> Two-way ANOVA\n\n")
  rt_anova_task <- aov(rt ~ boundary_position * stimulus_type,
                       data = df_task_task_labeled)
  print(summary(rt_anova_task))
  cat("\nTukey HSD post-hoc (boundary_position):\n")
  print(TukeyHSD(rt_anova_task, which = "boundary_position"))
} else {
  cat("Non-normality detected -> ART ANOVA\n\n")
  if (!requireNamespace("ARTool", quietly = TRUE))
    install.packages("ARTool", repos = "https://cloud.r-project.org")
  library(ARTool)
  art_model_task <- art(
    rt ~ boundary_position * stimulus_type + Error(participant_id),
    data = df_task_task_labeled
  )
  print(anova(art_model_task))
  cat("\nART pairwise contrasts:\n")
  print(summary(art.con(art_model_task, "boundary_position",
                        adjust = "bonferroni")))
}
```

## 3.8 REC and LDI Metrics

```{r exp3_rec_ldi}
participant_probs_task <- df_task_test %>%
  group_by(participant_id) %>%
  summarise(
    p_old_target   = mean(stimulus_type == "Target" & response_type == "Old"),
    p_old_foil     = mean(stimulus_type == "Foil"   & response_type == "Old"),
    p_similar_lure = mean(stimulus_type == "Lure"   & response_type == "Similar"),
    p_similar_foil = mean(stimulus_type == "Foil"   & response_type == "Similar"),
    .groups = "drop"
  )

mst_metrics_task <- participant_probs_task %>%
  mutate(REC_task = p_old_target - p_old_foil,
         LDI_task = p_similar_lure - p_similar_foil)
```

```{r exp3_rec_ldi_participant_table}
mst_metrics_task %>%
  select(participant_id, REC_task, LDI_task) %>%
  mutate(across(c(REC_task, LDI_task), ~ round(.x, 3))) %>%
  kable(caption = "Exp 3: Per-Participant REC and LDI") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp3_rec_ldi_summary_table}
mst_metrics_task %>%
  summarise(
    REC_mean = round(mean(REC_task), 3), REC_sd = round(sd(REC_task), 3),
    LDI_mean = round(mean(LDI_task), 3), LDI_sd = round(sd(LDI_task), 3)
  ) %>%
  kable(caption = "Exp 3: Group-Level REC and LDI Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, font_size = 12)
```

```{r exp3_rec_ldi_plot}
rec_ldi_plot(mst_metrics_task, "REC_task", "LDI_task",
             "Exp 3: Distribution of REC and LDI Scores")
```

## 3.9 Memory Accuracy: Join and Compute

```{r exp3_accuracy_join}
encoding_lookup_task <- df_task_task %>%
  select(participant_id, image_name, boundary_position)

df_task_joined <- df_task_test %>%
  left_join(encoding_lookup_task,
            by = c("participant_id", "image_name"),
            relationship = "many-to-many") %>%
  mutate(
    boundary_position = factor(boundary_position, levels = c("Non", "Pre", "Post")),
    lure_correct = (stimulus_type == "Lure"   & response_type == "Similar"),
    target_hit   = (stimulus_type == "Target" & response_type == "Old")
  )

boundary_perf_task <- df_task_joined %>%
  group_by(participant_id, boundary_position) %>%
  summarise(
    lure_CR    = mean(lure_correct, na.rm = TRUE),
    target_hit = mean(target_hit,   na.rm = TRUE),
    .groups    = "drop"
  )
```

## 3.10 Normality Check: Memory Accuracy

```{r exp3_accuracy_normality}
cells_lure_task <- boundary_perf_task %>%
  group_by(boundary_position) %>%
  summarise(vals = list(lure_CR), .groups = "drop") %>%
  mutate(label = paste("lure_CR |", boundary_position))

cells_target_task <- boundary_perf_task %>%
  group_by(boundary_position) %>%
  summarise(vals = list(target_hit), .groups = "drop") %>%
  mutate(label = paste("target_hit |", boundary_position))

normality_table(cells_lure_task,
                "Exp 3: Shapiro-Wilk - Lure Correct Rejection by Boundary")
normality_table(cells_target_task,
                "Exp 3: Shapiro-Wilk - Target Hit Rate by Boundary")
```

## 3.11 Memory Accuracy: Descriptive Statistics

```{r exp3_accuracy_desc_tables}
summary_table(boundary_perf_task,
              group_vars   = "boundary_position",
              dv           = "lure_CR",
              caption_text = "Exp 3: Lure Correct Rejection Rate by Boundary Position")

summary_table(boundary_perf_task,
              group_vars   = "boundary_position",
              dv           = "target_hit",
              caption_text = "Exp 3: Target Hit Rate by Boundary Position")
```

## 3.12 Memory Accuracy: Plots

```{r exp3_accuracy_violin}
boundary_perf_task %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  violin_box_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    facet_var = "measure",
    title     = "Exp 3: Memory Accuracy by Boundary Condition",
    subtitle  = "Diamond = group mean | Box = IQR | Violin = distribution",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

```{r exp3_accuracy_line}
boundary_perf_task %>%
  pivot_longer(cols = c(lure_CR, target_hit),
               names_to = "measure", values_to = "accuracy") %>%
  mutate(measure = recode(measure,
                          lure_CR    = "Lure Correct Rejection",
                          target_hit = "Target Hit")) %>%
  boundary_line_plot(
    x_var     = "boundary_position",
    y_var     = "accuracy",
    group_var = "measure",
    title     = "Exp 3: Memory Accuracy Trend Across Boundary Positions",
    subtitle  = "Error bars = +/- 1 SE",
    x_lab     = "Boundary Position",
    y_lab     = "Proportion Correct"
  )
```

## 3.13 Repeated Measures ANOVA

```{r exp3_rm_anova}
cat("--- RM-ANOVA: lure_CR ~ boundary_position ---\n")
rm_lure_task <- aov_ez(id = "participant_id", dv = "lure_CR",
                       data = boundary_perf_task, within = "boundary_position")
print(rm_lure_task)

cat("\n--- RM-ANOVA: target_hit ~ boundary_position ---\n")
rm_target_task <- aov_ez(id = "participant_id", dv = "target_hit",
                         data = boundary_perf_task, within = "boundary_position")
print(rm_target_task)
```

## 3.14 One-Sample Tests: Boundary vs Baseline

```{r exp3_one_sample}
perf_wide_task <- boundary_perf_task %>%
  pivot_wider(names_from = boundary_position,
              values_from = c(lure_CR, target_hit))

perf_diff_task <- perf_wide_task %>%
  mutate(
    lure_pre_diff    = lure_CR_Pre    - lure_CR_Non,
    lure_post_diff   = lure_CR_Post   - lure_CR_Non,
    target_pre_diff  = target_hit_Pre  - target_hit_Non,
    target_post_diff = target_hit_Post - target_hit_Non
  )

cat("=== lure_CR: Pre - Non ===\n")
one_sample_test(perf_diff_task$lure_pre_diff,    "lure Pre-Non (Exp3)")
cat("\n=== lure_CR: Post - Non ===\n")
one_sample_test(perf_diff_task$lure_post_diff,   "lure Post-Non (Exp3)")
cat("\n=== target_hit: Pre - Non ===\n")
one_sample_test(perf_diff_task$target_pre_diff,  "target Pre-Non (Exp3)")
cat("\n=== target_hit: Post - Non ===\n")
one_sample_test(perf_diff_task$target_post_diff, "target Post-Non (Exp3)")
```

```{r exp3_diff_plot}
diff_score_plot(perf_diff_task,
                "Exp 3: Difference Scores Relative to Non-Boundary Baseline")
```

## 3.15 Two-Sample Tests: Pre vs Post

```{r exp3_two_sample}
cat("=== lure_CR: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_task$lure_CR[boundary_perf_task$boundary_position == "Pre"],
  boundary_perf_task$lure_CR[boundary_perf_task$boundary_position == "Post"],
  "lure Pre (Exp3)", "lure Post (Exp3)"
)
cat("\n=== target_hit: Pre vs Post ===\n")
two_sample_test(
  boundary_perf_task$target_hit[boundary_perf_task$boundary_position == "Pre"],
  boundary_perf_task$target_hit[boundary_perf_task$boundary_position == "Post"],
  "target Pre (Exp3)", "target Post (Exp3)"
)
```
